---
title: "Supplemental Resource Heterogeneity Structures Microbial Communities"
author: "Mario E. Muscarella"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes:
   - \usepackage{array}
   - \usepackage{graphics}
   - \usepackage{booktabs}
output: 
  pdf_document:
    fig_caption: true
---

# Introduction
Community diversity is strongly affected by the bottom-up effects of resource availability. However, because resource pools often exist as heterogeneous mixtures of individual resources, resource heterogeneity may also affect the diversity of local communities. To test this hypothesis, we surveyed bacterial communities in lakes that spanned a resource concentration gradient. In addition, we characterized resource heterogeneity in these lakes using high-resolution mass spectrometry of the dissolved organic matter (DOM) pool. Using these data, we will test for relationships between the available resources and the aquatic heterotrophic bacteria community, and we will use co-occurrence analysis to test for bacteria-resource interactions. 

## Initial Setup
```{r, results='hide', message=FALSE, warning=FALSE}
rm(list=ls())
setwd("~/GitHub/ResourceHeterogeneity/analyses")

# Import Tools and Standard Functions
source("../bin/MothurTools.R")
source("../bin/CommonFunctions.R")

# Save Standard Plot Settings
opar <- par(no.readonly = TRUE)  # Saves plot defaults

# Load Required Packages
require("png"); require("grid");require("vegan"); require("igraph")
require("picante")# ;require("bioDist");require("gplots")
#require("xtable");require("phyloseq");require("car"); require("ade4");require("bioDist")
require("colorspace"); library("car")
source("../bin/box.cox.chord.R")
```

# Load Data & Minor Processing
## Lake Nutrient Concentrations and Physical Properties
```{r}
nuts <- read.csv(file = "../data/HMWF_Nutrients.txt", header = T)
chl <- read.delim(file = "../data/ChlorophyllA.txt", header = T)
chl <- chl[order(chl$Year, chl$Lake), ]
phys <- read.csv(file = "../data/lake_data2.txt", header = T)
all.equal(nuts$Site, chl$Lake); all.equal(nuts$Year, chl$Year);
all.equal(nuts$Site[nuts$Year == 2012], phys$Lake)
```


## Import Total Community
```{r}
# Define Inputs
# Design = general design file for experiment
# shared = OTU table from mothur with sequence similarity clustering
# Taxonomy = Taxonomic information for each OTU
design.in <- "../data/design.txt"
shared <- "../data/HMWF.final.opti.shared"
taxon  <- "../data/HMWF.final.opti.taxonomy"

# Import Design
design <- read.delim(design.in, header=T, row.names=1)
design <- design[design$Molecule == "DNA" & design$Year == "2012", ]

# Import Shared Files
OTUs.in <- read.otu(shared = shared, cutoff = "0.03")  

# Import Taxonomy
OTU.tax <- read.tax(taxonomy = taxon, format = "rdp")

# Remove Cyanobacteria
OTUs.in.2 <- OTUs.in[, -c(which(OTU.tax$Phylum == "Cyanobacteria/Chloroplast"))]
dim(OTUs.in.2)

OTU.tax.2 <- OTU.tax[which(OTU.tax$OTU %in% colnames(OTUs.in.2)), ]
table(OTU.tax.2$Class)
table(OTU.tax.2$Phylum)

# Data Transformations
# Reorder Site
OTUs.hmwf <- OTUs.in.2[rownames(design), ]

# Remove OTUs with less than two occurences across all sites
# OTUs <- OTUs.hmwf[, which(colSums(OTUs.hmwf) >= 2)]
OTUs <- OTUs.hmwf[, colSums((OTUs.hmwf > 0) * 1)  >= 2 | colSums(OTUs.hmwf) >= 3]
S.obs <- rowSums((OTUs > 0) * 1)

# Sequencing Coverage
coverage <- rowSums(OTUs)

bacteria <- dim(OTUs)[2]
dim(OTUs)

# Good's Coverage
goods.c <- goods(OTUs)

# Make Presence Absence Matrix
OTUsPA <- (OTUs > 0) * 1

# Make Relative Abundence Matrices
OTUsREL <- OTUs
for(i in 1:dim(OTUs)[1]){
  OTUsREL[i,] <- OTUs[i,]/sum(OTUs[i,])
}

# Log Transform Relative Abundances
OTUsREL.log <- suppressWarnings(decostand(OTUs, method="log"))

# Box-Cox Chord Transformation
OTUs.BCD <- box.cox.chord(OTUs)  #Log Chord Transformation
```

## Load DOM Profiles
```{r}
# Define Inputs
resource.neg <- "../data/SpecAbundAveNeg.csv"
annotations <- "../data/annotationSummary_MFconversion_output.csv"

# Import Resources
res.neg.in <- read.csv(resource.neg, header=T, row.names=1)
rownames(res.neg.in) <- c("Ann", "blank", "CanyonChemo", "Canyon", "CanyonHypo",
                      "CanyonI", "CanyonII", "CanyonIII", "CanyonIV", "Howe",
                      "Ives", "Jordan", "Lily", "Mountain", "Pony", "Rush",
                      "SecondPine", "UpperPine")

# Import Annotations
res.annot <- read.csv(annotations)

# Remove Blank and Extra Samples
blank.neg <- unlist(res.neg.in["blank", ])
res.hmwf.neg <- res.neg.in[-c(which(rownames(res.neg.in) %in% 
                            c("blank", "CanyonChemo", 
                              "CanyonHypo", "CanyonI", "CanyonII",
                              "CanyonIII", "CanyonIV", "Jordan"))), ]

# Remove Blank Peaks
for (i in 1:dim(res.hmwf.neg)[1]){
  res.hmwf.neg[i, ] <- res.hmwf.neg[i, ] - blank.neg * 1.1
}

# Remove Peaks Under Height of 50
res.hmwf.neg[res.hmwf.neg < 50] <- 0

# Remove Zero Sum Columns
res.hmwf.neg <- res.hmwf.neg[,colSums(res.hmwf.neg) > 0]

# Subset Annotations
missing.annot <- res.annot$Cmpd[which(res.annot$inferred.formula == 0)]
# res.hmwf.neg <- res.hmwf.neg[, -c(which(colnames(res.hmwf.neg) %in% missing.annot))]
res.annot <- res.annot[c(which(res.annot$Cmpd %in% colnames(res.hmwf.neg))), ]

# Data Transformations
# Reorder Sites
res.neg <- res.hmwf.neg[order(rownames(res.hmwf.neg)), ]

# Sequencing Coverage
coverage <- data.frame(Neg = rowSums(res.neg))
resources <- data.frame(Neg = dim(res.neg)[2])

# Make Relative Abundence Matrices
resREL.neg <- res.neg
for(i in 1:dim(res.neg)[1]){
  resREL.neg[i,] <- res.neg[i,]/sum(res.neg[i,])
}

# Log Transform Relative Resource Abundance
resREL.neg.log <- suppressWarnings(decostand(resREL.neg, method="log"))

# Box-Cox Chord Transformation
DOM.BCD <- box.cox.chord(res.neg)  #Log Chord Transformation
```

## DOM Alpha Diversity 
```{r}
# Observed Richness
S.res <- rowSums((res.neg > 0) * 1)

# Simpson's Evenness
res.simpsE <- round(apply(res.neg, 1, SimpE), 3)

# Shannon's Diversity
res.shan <- round(vegan::diversity(res.neg, index = "shannon"), 2)

# Combine Alpha Diversity
res.div <- data.frame("Lake" = row.names(res.neg), S.res, res.simpsE, res.shan)

# Summary Stats
range(res.div$S.res);range(res.div$res.shan);range(res.div$res.simpsE)
CV(res.div$S.res);CV(res.div$res.shan);CV(res.div$res.simpsE)
```

## DOM Beta Diversity
```{r}
# Calculate Bray-Curtis 
hmwf.bray.res <- vegdist(resREL.neg, method = "bray")
hmwf.bray.res.log <- vegdist(resREL.neg.log, method = "bray")

dis.mean <- mean(hmwf.bray.res)
dis.mean.l <- mean(hmwf.bray.res.log)

hmwf.bcd.res <- vegdist(DOM.BCD, method = "euclidean")
dis.mean.b <- mean(hmwf.bcd.res)

# Principal Coordinates Analysis
pcoa.res <- cmdscale(hmwf.bray.res, eig = TRUE, k = 3) 
explainvar1.res <- round(pcoa.res$eig[1] / sum(pcoa.res$eig), 3) * 100
explainvar2.res <- round(pcoa.res$eig[2] / sum(pcoa.res$eig), 3) * 100
explainvar3.res <- round(pcoa.res$eig[3] / sum(pcoa.res$eig), 3) * 100
sum.eig.res <- sum(explainvar1.res, explainvar2.res, explainvar3.res)
```


# Community Alpha Diversity
```{r}
# Total Community Alpha# Observed Richness
S.obs <- rowSums((OTUs > 0) * 1)

# Simpson's Evenness
simpsE <- round(apply(OTUs, 1, SimpE), 3)

# Shannon's Diversity
shan <- vegan::diversity(OTUs, index = "shannon")

# Rarefied Richness
OTUs.rar <- rrarefy(OTUs, ceiling(min(rowSums(OTUs)) * 0.9))
S.rar <- round(rarefy(OTUs, ceiling(min(rowSums(OTUs)) * 0.9)), 0)

# Simpson's Evenness
simpsE.rar <- round(apply(OTUs.rar, 1, SimpE), 3)

# Shannon's Diversity
shan.rar <- vegan::diversity(OTUs.rar, index = "shannon")

alpha.div <- cbind(design, S.obs, simpsE, shan, S.rar, simpsE.rar, shan.rar)
alpha.div <- alpha.div[order(alpha.div$Lake, alpha.div$Year, alpha.div$Molecule), ]

# Organize Data
nuts2 <- nuts[nuts$Year == 2012, ]
nuts2 <- nuts2[order(nuts2$Site), ]

all.equal(nuts2$Site, alpha.div$Lake)
all.equal(nuts2$Site, res.div$Lake)
all.equal(nuts2$Site, phys$Lake)

dat <- data.frame(alpha.div[, c(1, 4:8)], res.div[, 2:4], 
                  nuts2[, 3:5], phys[, c(4,5,7,9)], 
                  row.names = alpha.div[, 1])

shapiro.test(dat$DOC)  # Not Normal
shapiro.test(dat$S.rar) # Not Normal
shapiro.test(dat$simpsE.rar) # Normal
shapiro.test(dat$S.res) # Normal

# Without Pony or Lily
shapiro.test(dat$DOC[dat$DOC < 10]) # Normal
shapiro.test(dat$S.rar[dat$DOC < 10]) # Normal

# Transform DOC and S.rar with Box-Cox
D.power <- powerTransform(dat$DOC)
S.power <- powerTransform(dat$S.rar)
dat$DOC.t <- as.numeric(scale(bcPower(dat$DOC, coef(D.power, round =F))))
dat$S.rar.t <- as.numeric(scale(bcPower(dat$S.rar, coef(S.power, round =F))))
shapiro.test(dat$DOC.t) # Normal
shapiro.test(dat$S.rar.t) # Normal

# Resource Heterogeneity and Divesity
mod3 <- lm(S.rar.t ~ S.res, data = dat)
mod4 <- lm(simpsE.rar ~ S.res, data = dat)
summary(mod3);summary(mod4)

mod4.p <- round(summary(mod4)$coefficients[2,4], 3)

pred.frame2 <- data.frame(S.res = seq(525, 572, 1))

png(filename="../figures/FigureS7.png",
    width = 900, height = 900, res = 96*2, bg = "white")
par(opar)

par(mar = c(0.5, 1, 1, 1) + 0.1, oma = c(5, 6, 0, 0) + 0.1)

# Resource Richness vs Species Eveness
plot(dat$simpsE.rar ~ dat$S.res,
     xlab = "", ylab = "", type = "n", axes = F,
     xlim = c(525, 572), ylim = c(0, 0.07), las = 1,
     pch = 22, col = "black", bg = "gray", cex = 2, lwd = 2)
add.hull(model = mod4, pred.frame = pred.frame2)
matlines(pred.frame2, predict(mod4, interval = "c", newdata=pred.frame2),
         lty=c(2,3,3), lwd=c(4,2,2), col="black")
points(dat$simpsE.rar ~ dat$S.res,
       pch = 22, col = "black", bg = "gray", cex = 1.5, lwd = 2)
legend("topleft", legend = bquote(italic(p) == .(mod4.p)), 
       bty = "n", cex = 1.25, inset = c(-0.05, 0.01))
mtext("# DOM Components", side = 1, line = 3.5, cex = 1.5)
mtext("OTU Evenness\n(Total Community)", side = 2, line = 4, cex = 1.5)
axis(1, lwd = 2, labels = T, las = 1, at = c(seq(520, 570, 10)), cex.axis = 1.25)
axis(2, lwd = 2, labels = T, las = 1, at = c(seq(0, 0.06, 0.02)), cex.axis = 1.25)
axis(3, lwd = 2, tck = -0.02, labels = F, at = c(seq(520, 570, 10)))
axis(4, lwd = 2, tck = -0.02, labels = F, at = c(seq(0, 0.06, 0.02)))
axis(1, lwd = 2, tck = 0.02, labels = F, at = c(seq(520, 570, 10)))
axis(2, lwd = 2, tck = 0.02, labels = F, at = c(seq(0, 0.06, 0.02)))
axis(3, lwd = 2, tck = 0.02, labels = F, at = c(seq(520, 570, 10)))
axis(4, lwd = 2, tck = 0.02, labels = F, at = c(seq(0, 0.06, 0.02)))
box(lwd = 2)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices

img <- readPNG("../figures/FigureS7.png")
grid.raster(img)

```

# Community Beta Diversity
```{r}

# Total Community Beta
bray.BAC <- vegdist(decostand(OTUsREL, "log"), "bray")
pcoa.BAC <- cmdscale(bray.BAC, k = 3, eig = T)
bray.RES <- vegdist(decostand(resREL.neg, "log"), "bray")
pcoa.RES <- cmdscale(bray.RES, k = 3, eig = T)
dbRDA.dom <- capscale(bray.BAC ~ pcoa.RES$points[, 1:3], add = T)
anova(dbRDA.dom)
RsquareAdj(dbRDA.dom)
anova(dbRDA.dom, by = 'axis')
res.com <- envfit(pcoa.BAC, pcoa.RES$points)
res.com

cor.test(~ pcoa.RES$points[, 1] + dat$DOC.t)
cor.test(~ pcoa.RES$points[, 2] + dat$DOC.t)
cor.test(~ pcoa.RES$points[, 3] + dat$DOC.t)

# Resource Concentration dbRDA
hmwf.bray.REL <- vegdist(OTUsREL.log, method = "bray")
pcoa.rel <- cmdscale(hmwf.bray.REL, eig = TRUE, k = 3) 
dbRDA <- capscale(hmwf.bray.REL ~ dat$DOC.t, comm = OTUsREL.log, add = T)
anova(dbRDA, permutations = how(nperm=9999))
RsquareAdj(dbRDA)

# DOM Diversity dbRDA; using: hmwf.bray.res; pcoa.res
# Calculate Bray-Curtis 
hmwf.bray.res <- vegdist(resREL.neg, method = "bray")
hmwf.bray.res.log <- vegdist(resREL.neg.log, method = "bray")
hmwf.bcd.res <- vegdist(box.cox.chord(res.neg), method = "euclidean")
pcoa.res <- cmdscale(hmwf.bray.res.log, eig = TRUE, k = 3) 
dbRDA.dom <- capscale(hmwf.bray.REL ~ pcoa.res$points[, 1:3], add = T)
anova(dbRDA.dom)
RsquareAdj(dbRDA.dom)

anova(dbRDA.dom, by = 'axis')

# PCoA of Total Community
bray.BAC <- vegdist(decostand(OTUsREL, "log"), "bray")
pcoa.BAC <- cmdscale(bray.BAC, k = 3, eig = T)
explainvar1 <- round(pcoa.BAC$eig[1] / sum(pcoa.BAC$eig), 3) * 100
explainvar2 <- round(pcoa.BAC$eig[2] / sum(pcoa.BAC$eig), 3) * 100

# PCoA of Resources
bray.RES <- vegdist(decostand(resREL.neg, "log"), "bray")
pcoa.RES <- cmdscale(bray.RES, k = 3, eig = T)

# Resource Concentrations
cons.RES <- dat$DOC.t

# Initial Plot as PNG
png(filename="../figures/FigureS8.png",
    width = 1300, height = 900, res = 96*2, bg = "white")

# Define Plot Parameters
par(opar)
par(mar = c(4.75, 5, 1, 1) + 0.5)

# Initiate Plot 1
plot(pcoa.BAC$points[ ,1], pcoa.BAC$points[ ,2], 
     ylim = c(-0.3, 0.4), xlim = c(-0.4, 0.6), 
     xlab = paste("PCoA 1 (", explainvar1, "%)", sep = ""),
     ylab = paste("PCoA 2 (", explainvar2, "%)", sep = ""),
     #xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     pch = 22, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1, 
     axes = FALSE)

# Add Axes
axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1.25, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1.25, las = 1, 
     at = c(-0.2, 0, 0.2, 0.4))
axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02, 
     at = c(-0.2, 0, 0.2, 0.4))
axis(side = 1, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 2, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01, 
     at = c(-0.2, 0, 0.2, 0.4))
axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01, 
     at = c(-0.2, 0, 0.2, 0.4))
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)
  
# Add Points & Labels
points(pcoa.BAC$points[ ,1], pcoa.BAC$points[ ,2], pch = 22, 
       cex = 2.5, bg = "gray", lwd = 2)

text(pcoa.BAC$points[ ,1] + 
       c(0.04, 0, 0, 0, 0, 0, 0, -0.04, -0.02, 0.02), 
     pcoa.BAC$points[ ,2] + 
       c(-0.04, 0.04, 0.04, -0.04, 0.04, 0.04, 0.04, -0.04, 0.04, -0.04), 
     labels = dat$Lake, , col = "black", cex = 0.8)

# DOM Composition Vectors
cor.test(~ pcoa.RES$points[, 2] + pcoa.BAC$points[, 1])
res.com <- envfit(pcoa.BAC, pcoa.RES$points[,1:2])
com.arrows <- res.com[[1]]$arrows * 0.3
arrows(0, 0, -com.arrows[1, 1], com.arrows[1, 2], 
       col = "gray30", length = 0.1, lwd = 4)
arrows(0, 0, -com.arrows[2, 1], -com.arrows[2, 2], 
       col = "gray30", length = 0.1, lwd = 4)
text(-com.arrows[1, 1] - 0.02, com.arrows[1, 2] * 1.2, "DOM 1", 
     col = "gray40", cex = 1.25, font = 3)
text(-com.arrows[2, 1] * 1.2, com.arrows[2, 2] + 0.08, "DOM 2", 
     col = "gray40", cex = 1.25, font = 3)


dev.off() # this writes plot to folder
graphics.off() # shuts down open devices

img <- readPNG("../figures/FigureS8.png")
grid.raster(img)


```

