---
title: "Resource Heterogeneity Structures Microbial Communities"
author: "Mario E. Muscarella"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes:
   - \usepackage{array}
   - \usepackage{graphics}
   - \usepackage{booktabs}
output: 
  pdf_document:
    fig_caption: true
---

# Introduction
Much is already know about how spatial gradients in resource availability contribution to the structure and fucntion of microbial communities.
However, we are begining to appreciate the molecular diversity within the resource pool.
Resources can be just as diverse as consumers and differ in their quality and availability to consumers.
As such, resource diverse represents a mechanisms to understand spatial distirubitons of consumers.
In this study, we explore how both the concentration and diversity of resources contribute to the structure and function of aquatic microbial communities. 

We explore three hypotheses:

1. Is there a relationship between resource concentration and diversity?
  + Dilution Hypothesis: Arrieta et al. 2015 Science
  
2. Do the concentrations and diversity of resources explain differences between communities?
  + Resource Heterogeneity Hypothesis
  
3. Do concentration and diversity explain different aspects of diversity
  + Grinnellian (environmental habitat) vs. Eltonian (food habitat) Niche Hypothesis
  + Resource Substitution Hypothesis

## Initial Setup
```{r, results='hide', message=FALSE}
rm(list=ls())
getwd()
setwd("~/GitHub/ResourceHeterogeneity/analyses")

# Import Tools and Standard Functions
source("../bin/MothurTools.R")
se <- function(x, ...){sd(x, na.rm = TRUE)/sqrt(length(na.omit(x)))}

# Save Standard Plot Settings
opar <- par(no.readonly = TRUE)  # Saves plot defaults

# Load Required Packages
require("xtable")
require("png")
require("grid")
require("vegan")
require("RgoogleMaps")
library("maps")
library("mapdata")
require("maptools")
require("picante")
require("phyloseq")
require("car")
require("colorspace")
```

# Study System
We sampled 10 lakes in the Huron Mountains of Michigan. 
The Huron Mountains are located in the Superior Bedrock Uplands region of the Michigan Upper Peninsula (Schaetzl et al 2013).

The region is classified as Superior Bedrock Uplands
The forests around the lakes are old-growth hemlock-nothern hardwoods (Kerry Woods)
The lakes are part of the Pine River Watershed which drains into Lake Superior (see: www.co.marquette.mi.us/departments/plannings/docs/watershed.pdf)

## Water Body Physical Information
***Add Temperature***
***Add Coordinates***
```{r}
lake.data <- read.csv("../data/lake_data.txt", row.names=1)
colnames(lake.data) <- c("depth", "pH", "DO1", "DO2")
lake.data$area <- rep(NA, dim(lake.data)[1])
```

## Study System Map
```{r}
# Shape file source: http://www.mcgi.state.mi.us/mgdl/?rel=ext&action=sext
shape <- readShapePoly("../data/lake_polygons_200403/lake_polygons_200403.shp", 
                       IDvar = "UNIQUE_ID")

# Extract Areas
grp.opt <- shape$COUNTY == "Marquette" & shape$FMU == "LSW"
lake.data$area[1] <- shape$AREA[which(shape$NAME == "Lake Ann" & grp.opt)]
lake.data$area[2] <- shape$AREA[which(shape$NAME == "Canyon Lake" & grp.opt)]
lake.data$area[3] <- shape$AREA[which(shape$NAME == "Howe Lake" & grp.opt)]
lake.data$area[4] <- shape$AREA[which(shape$NAME == "Ives Lake" & grp.opt)]
lake.data$area[5] <- shape$AREA[which(shape$NAME == "Lily Pond" & grp.opt)]
lake.data$area[6] <- shape$AREA[which(shape$NAME == "Mountain Lake" & grp.opt)]
lake.data$area[7] <- 2000 # estimate...smallest and not in GIS dataset
lake.data$area[8] <- shape$AREA[which(shape$NAME == "Rush Lake" & grp.opt)]
lake.data$area[9] <- shape$AREA[which(shape$NAME == "Second Lake" & grp.opt)]
lake.data$area[10] <- shape$AREA[which(shape$NAME == "Third Lake" & grp.opt)]

# Convert sq m to sq km
lake.data$area <- lake.data$area / 1000000

# Notes on how to get shapefile info
# str(shape, max.level=4)
# Attempt to find Pony
# plot(shape[which(shape$LAKE_NAME == "no name" & 
# shape$COUNTY == "Marquette" & shape$FMU == "LSW"), ])

# Plot from shapefile (just to check)
#  grp.opts <- shape$COUNTY == "Marquette" & shape$FMU == "LSW"
#  plot(shape[c(
#   which(shape$NAME == "Ives Lake" & grp.opts),
#   which(shape$NAME == "Mountain Lake" & grp.opts),
#   which(shape$NAME == "Howe Lake" & grp.opts),
#   which(shape$NAME == "Rush Lake" & grp.opts),
#   which(shape$NAME == "Lake Ann" & grp.opts),
#   which(shape$NAME == "Canyon Lake" & grp.opts),
#   which(shape$NAME == "Lily Pond" & grp.opts),
#   which(shape$NAME == "Second Lake" & grp.opts),
#   which(shape$NAME == "Third Lake" & grp.opts)),])

lake.data <- lake.data[sort(row.names(lake.data)), c("area", "pH")]
```

## Table 1: Lake Physical Properties
```{r, results="asis"}
addtorow <- list()
addtorow$pos <- list(0)
addtorow$command <- c("Lake & Area (Km$^2$)  & pH \\\\\n")
lake.tab <- xtable(lake.data, digits = c(0,1,3))
align(lake.tab) <- "ccc"
print(lake.tab, add.to.row = addtorow, include.colnames = FALSE, 
      type= "latex", file="../tables/Table1.tex", 
      hline.after = c(-1, -1, 0, nrow(lake.tab)))
print(lake.tab, add.to.row = addtorow, include.colnames = FALSE, 
      comment = FALSE, hline.after = c(-1, -1, 0, nrow(lake.tab)))
```

## Figure 1: Study System Map
```{r, results='hide'}
png(filename="../figures/Figure1.png",
    width = 1800, height = 900, res = 96*2)
par(opar)
par(mfrow = c(1,1), mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0) + 0.5)

newmap1 <- GetMap(center = c(46.86, -87.93), zoom = 13, 
                 maptype = "terrain", GRAYSCALE = FALSE, frame = FALSE,
                 path = "&style=feature:all|element:labels|visibility:off")
newmap2 <- GetMap(center = c(46.86, -87.82), zoom = 13, 
                 maptype = "terrain", GRAYSCALE = FALSE, frame = FALSE,
                 path = "&style=feature:all|element:labels|visibility:off")

layout( matrix(c(1,1,1,1,1,1,
                 1,1,1,1,1,1,
                 1,1,1,1,1,1,
                 2,2,2,2,2,2,
                 2,2,2,3,3,3,
                 2,2,2,3,3,3), 6, 6, byrow = FALSE),
        widths = rep(2, 6), heights = rep(2, 6))

# Left Side
PlotOnStaticMap(newmap1, zoom = 13, cex = 2, col = "blue")
text(-120, 270, "Howe", col="red", cex=1.2)
text(100, 255, "Rush", col="red", cex=1.2)
text(105, 55, "Mountain", col="red", cex=1.2)
arrows(10, 100, x1 = -10, y1 = 100, length=0.05, col = "red", lwd = 2, code = 1)
text(-36, 100, "Ann", col="red", cex=1.2)
arrows(60, 230, x1 = 40, y1 = 230, length=0.05, col = "red", lwd = 2, code = 1)
text(8, 230, "Pony", col="red", cex=1.2)
arrows(55, -230, x1 = 75, y1 = -230, length=0.05, col = "red", lwd = 2, code = 1)
text(120, -230, "Canyon", col="red", cex=1.2)

# Right Side
PlotOnStaticMap(newmap2, zoom = 13, cex = 2, col = "blue")
text(-180, -90, "Ives", col="red", cex=1.2)
arrows(-160, 20, x1 = -140, y1 = 20, length = 0.05, col = "red", lwd = 2, code = 1)
text(-75, 20, "Upper Pine", col="red", cex = 1.2)
arrows(-220, 80, x1 = -200, y1 = 80, length = 0.05, col = "red", lwd = 2, code = 1)
text(-125, 80, "Second Pine", col="red", cex = 1.2)
arrows(-55, -105, x1 = -35, y1 = -105, length = 0.05, col = "red", lwd = 2, code = 1)
text(-12, -105, "Lily", col="red", cex=1.2)

# Compass Arrow
arrows(280, 280, 280, 240, length = 0.1, col = "black", lwd = 3, code = 1)
text(280, 220, "N", col = "black", cex = 1.5)

# Inset
map("state", "Michigan", col = "gray80", fill = TRUE, 
    xlim = c(-92,-82), ylim = c(41, 48))
points(-87.89, 46.8, pch = 20, col = "red")

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices 
par(opar)
```

```{r fig.width=7, fig.height=3.5,echo=FALSE,fig.cap="Study System Map"}
img <- readPNG("../figures/Figure1.png")
grid.raster(img)
```

This study system is know to have differences in the concentrations of growth limiting nutrients.
Specifically, the concentrations of dissolved organic carbon and phosphorus differ between the lakes.
We also have data for total nitrogen, but the values are odd and may not be reasonable for interpretation.
The reason the nitrogen values are odd is because many were at the lower detection level of the instrument.

# Lake Nutrient Concentrations
```{r}
# DOC
DOC2011 <- read.delim("../data/2011DOC_data.txt", header=T)
DOC2012 <- read.delim("../data/2012DOC_data.txt", header=T)
DOC <- rbind(DOC2011, DOC2012)
DOC <- DOC[grep("MEM*", DOC$Sample), ]
colnames(DOC) <- c("sample", "conc", "LCL", "UCL", "se")
DOCkey <- read.delim("../data/DOC_KEY_epi.txt", header=T)
DOC$code <- DOC$sample
DOC <- DOC[which(DOC$code %in% DOCkey$Sample.Name), ]
DOC$sample <- DOCkey$Site[match(DOCkey$Sample.Name, DOC$code)]
DOC$year <- substr(DOC$code, 4, 7)
DOC$conc <- pmax(DOC$conc, 0)
DOC2 <- data.frame("sample" = DOC$sample, "year" = DOC$year, 
                   "conc" =  DOC$conc)[order(DOC$sample, DOC$year), ]
DOC$sample[grep("Pony", DOC$sample)] <- "Pony"
DOC <- droplevels(DOC)

# Total Nitrogen
TN <- read.delim("../data/HMWF_TN.txt")
colnames(TN) <- c("sample", "year", "conc")
TN2 <- data.frame("sample" = TN$sample, "year" = TN$year, 
                  "conc" = TN$conc)[order(TN$sample, TN$year), ]
TN <- droplevels(TN)

# Total Phosphorus
TP2011 <- read.delim("../data/2011TP_data.txt")
TP2012 <- read.delim("../data/2012TP_data.txt")
TP2011$year <- rep("2011", dim(TP2011)[1])
TP2012$year <- rep("2012", dim(TP2012)[1])
TP <- rbind(TP2011, TP2012)
TP <- TP[grep("*iltered", TP$Sample), ]
colnames(TP) <- c("sample", "conc", "LCL", "UCL", "se", "year")
TP$code <- TP$sample
TDP <- TP[grep("*Filtered", TP$sample), ]
TP <- TP[grep("*Unfiltered", TP$sample), ]
TP$sample <- gsub(" Unfiltered", "", TP$sample)
TDP$sample <- gsub(" Filtered", "", TDP$sample)
TP[6, ] <- TDP[6, ]
TP <- TP[-c(which(TP$sample == "CanyonHypo" | TP$sample == "CanyonChemo")), ]
TP$sample <- gsub("CanyonEpi", "Canyon", TP$sample)
TP$sample <- as.factor(TP$sample)
TP$conc <- pmax(TP$conc, 0)
TP2 <- data.frame("sample" = TP$sample, "year" = TP$year, 
                  "conc" = TP$conc)[order(TP$sample, TP$year), ]
TP$sample[grep("Pony", TP$sample)] <- "Pony"
TP <- droplevels(TP)
```

## Organize Data Table
```{r}
DOC2 <- aggregate(conc ~ sample + year, DOC2, mean)
TN2 <- aggregate(conc ~ sample + year, TN2, mean)
TP2 <- aggregate(conc ~ sample + year, TP2, mean)

nuts <- data.frame("sample" = DOC2$sample, "year" = DOC2$year, 
              "DOC" = DOC2$conc, "TP" = TP2$conc)

nuts <- data.frame(nuts[-which(nuts$sample == "Pony.N"), ])
nuts$sample[grep("Pony", nuts$sample)] <- "Pony"
nuts <- droplevels(nuts)
nuts$TN <- TN2$conc
```

## Statistical Tests of Nutrients
```{r}
a.tn <- Anova(lm(TN ~ as.factor(sample) + as.factor(year), data = nuts))
a.doc <- Anova(lm(DOC ~ as.factor(sample) + as.factor(year), data = nuts))
a.tp <- Anova(lm(TP ~ as.factor(sample) + as.factor(year), data = nuts))
```

## Table 2: Lake Nutrients
```{r, results="asis"}
nuts2 <- data.frame(matrix(NA, 10, 6))
row.names(nuts2) <- levels(nuts$sample)
colnames(nuts2) <- c("DOC11", "DOC12", "TP11", "TP12", "TN11", "TN12")
for (i in row.names(nuts2)){
  nuts2[i, 1] <- round(nuts[nuts$sample == i & nuts$year == "2011", 3], 2)
  nuts2[i, 2] <- round(nuts[nuts$sample == i & nuts$year == "2012", 3], 2)
  nuts2[i, 3] <- round(nuts[nuts$sample == i & nuts$year == "2011", 4], 2)    
  nuts2[i, 4] <- round(nuts[nuts$sample == i & nuts$year == "2012", 4], 2)
  nuts2[i, 5] <- round(nuts[nuts$sample == i & nuts$year == "2011", 5], 2)    
  nuts2[i, 6] <- round(nuts[nuts$sample == i & nuts$year == "2012", 5], 2)
}

addtorow <- list()
addtorow$pos <- list(0, 0, 0)
addtorow$command <- c(" & \\multicolumn{2}{c}{DOC} & 
                      \\multicolumn{2}{c}{TP} & 
                      \\multicolumn{2}{c}{TN}\\\\\n", 
                      "Lake & \\multicolumn{2}{c}{(mg C L$^{-1}$)} & 
                      \\multicolumn{2}{c}{($\\mu$g P L$^{-1}$)} & 
                      \\multicolumn{2}{c}{(mg N L$^{-1}$)}\\\\\n",
                      " & 2011 & 2012 & 2011 & 2012 & 2011 & 2012 \\\\\n")
nut.tab <- xtable(nuts2)
align(nut.tab) <- "crrrrrr"
print(nut.tab, add.to.row = addtorow, include.colnames = FALSE, 
      type= "latex", file="../tables/Table2.tex", 
      hline.after = c(-1, -1, 0, nrow(nut.tab)))
print(nut.tab, add.to.row = addtorow, include.colnames = FALSE, 
      comment = FALSE, hline.after = c(-1, -1, 0, nrow(nut.tab)))
```


# Patterns of Bacterial Diversity
The major difference that we are interested in is bacterial diversity across the sites.
We know that the lakes have different microbiomes.
These microbiomes can be influenced by physical, chemical and biological interactions within each lake.

## Import Raw Data
```{r}
# Define Inputs
# Design = general design file for experiment
# shared = OTU table from mothur with sequence similarity clustering
# Taxonomy = Taxonomic information for each OTU
design.in <- "../data/design.txt"
shared <- "../data/HMWF.bac.final.shared"
taxon  <- "../data/HMWF.bac.final.0.03.taxonomy"

# Import Design
design <- read.delim(design.in, header=T, row.names=1)

# Import Shared Files
OTUs.in <- read.otu(shared = shared, cutoff = "0.03")    # 97% Similarity

# Import Taxonomy
OTU.tax <- read.tax(taxonomy = taxon, format = "rdp")
```

## Data Transformations
```{r}
# Reorder Site
OTUs.hmwf <- OTUs.in[rownames(design), ]

# Remove OTUs with less than two occurences across all sites
# OTUs <- OTUs.hmwf[, which(colSums(OTUs.hmwf) >= 2)]
OTUs <- OTUs.hmwf[, colSums((OTUs.hmwf > 0) * 1)  >= 2 | colSums(OTUs.hmwf >= 10)]

# Sequencing Coverage
coverage <- rowSums(OTUs)

# Good's Coverage
goods <- function(x = ""){
  1 - (sum(x == 1) / rowSums(x))
}
goods.c <- goods(OTUs)

# Make Presence Absence Matrix
OTUsPA <- (OTUs > 0) * 1

# Make Relative Abundence Matrices
OTUsREL <- OTUs
for(i in 1:dim(OTUs)[1]){
  OTUsREL[i,] <- OTUs[i,]/sum(OTUs[i,])
}

# Log Transform Relative Abundances
OTUsREL.log <- decostand(OTUs, method="log")
```

## Calculate Alpha Diversity
```{r}
# Observed Richness
S.obs <- rowSums((OTUs > 0) * 1)

# Simpson's Evenness
SimpE <- function(x = ""){
  x <- as.data.frame(x)
  D <- diversity(x, "inv")
  S <- sum((x > 0) * 1) 
  E <- (D)/S 
  return(E)
}
simpsE <- round(apply(OTUs, 1, SimpE), 3)

# Shannon's Diversity
H <- function(x = ""){
  x <- x[x>0]
  H = 0
  for (n_i in x){
    p = n_i / sum(x)
    H = H - p*log(p) 
  }
  return(H)
}

shan <- round(apply(OTUs, 1, H), 2)
shan2 <- diversity(OTUs, index = "shannon")

# Rarefied Richness
S.rar <- round(rarefy(OTUs, min(rowSums(OTUs))), 0)

design <- droplevels(design)

alpha.div <- cbind(design, S.obs, simpsE, shan, S.rar)
alpha.div <- alpha.div[order(alpha.div$Lake, alpha.div$Year, alpha.div$Molecule), ]
```

## Alpha Diversity Statistics
```{r}
alpha.div
div.mod1 <- aov(S.obs ~ Lake, data = alpha.div)
TukeyHSD(div.mod1)
div.mod2 <- aov(simpsE ~ Lake, data = alpha.div)
TukeyHSD(div.mod2)
div.mod3 <- aov(S.rar ~ Lake + Molecule, data = alpha.div)
TukeyHSD(div.mod3)
div.mod3 <- lm(S.rar ~ Lake + Molecule, data = alpha.div)
Anova(div.mod3)
div.mod4 <- aov(S.rar ~ Lake + as.factor(Year), data = alpha.div)
TukeyHSD(div.mod4)
div.mod5 <- aov(S.rar ~ Lake, data = alpha.div[alpha.div$Lake != "Pony" & 
                                                alpha.div$Lake != "Lily", ])
div.mod5 <- lm(S.rar ~ Lake + Molecule, data = alpha.div[alpha.div$Lake != "Pony" & 
                                                alpha.div$Lake != "Lily", ])
Anova(div.mod5)
```

## Lake Phylogenetic Diversity
```{r}
# Import Tree with *ape* 
hmwf.tree <- read.tree("../fasttree/HMWF.bac.0.03.gg.tree")
# tips <- paste(rep("Otu", length(hmwf.tree$tip.label)), 
#               formatC(seq(1:length(hmwf.tree$tip.label)), 
#                       width = 6, format = "d", flag = "0"), sep = "")
# hmwf.tree$tip.label <- tips
prunedTree <- prune.sample(OTUs,hmwf.tree)
OTUs.rar <- rrarefy(OTUs, sample = min(rowSums(OTUs)))

faiths <- pd(OTUs, prunedTree, include.root = FALSE)
# ses.pd(OTUs, prunedTree, include.root = FALSE, null.model = "independentswap", runs = 9, iterations = 10)
PSR <- psr(OTUs, prunedTree, compute.var = F)
PSR <- psr(OTUs.rar, prunedTree, compute.var = F)
PSD <- psd(OTUs, prunedTree, compute.var = F)
# specaccum.psr(OTUs, prunedTree, permutations = 100, method = "random")
plot(faiths$PD ~ faiths$SR)
plot(PSR$PSR ~ PSR$SR)
```

## Phylogenetic Diversity Statistics
```{r}
faiths2 <- cbind(faiths, alpha.div)
phy.mod1 <- aov(PD ~ Lake, data = faiths2)
summary(phy.mod1)
TukeyHSD(phy.mod1)
phy.mod2 <- aov(PD ~ Lake + Molecule, data = faiths2[faiths2$Lake != "Pony" & 
                                                faiths2$Lake != "Lily", ])
summary(phy.mod2)
phy.mod3 <- aov(PD ~ Lake + Molecule, data = faiths2)
summary(phy.mod3)
phy.mod4 <- lm(PD ~ Lake + Molecule, data = faiths2)

DNA.PD <- mean(faiths2$PD[faiths2$Molecule == "DNA"])
RNA.PD <- mean(faiths2$PD[faiths2$Molecule == "RNA"])

phy.mod4 <- lm(PD ~ SR + Lake + Molecule, data = faiths2)
Anova(phy.mod4)

```

## Table 4: Bacterial Diversity
```{r, results="asis"}
div.raw <- cbind(alpha.div, faiths)
div <- data.frame(matrix(NA, ncol = 9, nrow = 10))
colnames(div) <- c("Lake", "SR_T_11", "SR_T_12", "PR_T_11", "PR_T_12", 
                   "SR_A_11", "SR_A_12", "PR_A_11", "PR_A_12")
row.names(div) <- div.raw$Lake[div.raw$Molecule == "DNA" & div.raw$Year == 2011]
div[, 1] <- div.raw$S.rar[div.raw$Molecule == "DNA" & div.raw$Year == 2011]
div[, 2] <- div.raw$S.rar[div.raw$Molecule == "DNA" & div.raw$Year == 2012]
div[, 3] <- div.raw$PD[div.raw$Molecule == "DNA" & div.raw$Year == 2011]
div[, 4] <- div.raw$PD[div.raw$Molecule == "DNA" & div.raw$Year == 2012]
div[, 5] <- div.raw$S.rar[div.raw$Molecule == "RNA" & div.raw$Year == 2011]
div[, 6] <- div.raw$S.rar[div.raw$Molecule == "RNA" & div.raw$Year == 2012]
div[, 7] <- div.raw$PD[div.raw$Molecule == "RNA" & div.raw$Year == 2011]
div[, 8] <- div.raw$PD[div.raw$Molecule == "RNA" & div.raw$Year == 2012]

div[, 1:8] <- round(div[, 1:8], 0)

addtorow <- list()
addtorow$pos <- list(0, 0, 0)
addtorow$command <- c(" & \\multicolumn{4}{c}{Total} & 
                      \\multicolumn{4}{c}{Active} \\\\\n",
                      "Lake & \\multicolumn{2}{c}{S\\textsubscript{spec}} & 
                      \\multicolumn{2}{c}{S\\textsubscript{phy}} & 
                      \\multicolumn{2}{c}{S\\textsubscript{spec}} &
                      \\multicolumn{2}{c}{S\\textsubscript{phy}} \\\\\n", 
                      " & 2011 & 2012 & 2011 & 2012 & 
                      2011 & 2012 & 2011 & 2012 \\\\\n")
div.tab <- xtable(div, auto = TRUE)
align(div.tab) <- c("c ","r ", "r ", "r ", "r "," r ", "r ", "r ", "r ", "r ")
print(div.tab, add.to.row = addtorow, include.colnames = FALSE, 
      type= "latex", file="../tables/Table4.tex", 
      hline.after = c(-1, -1, 0, nrow(div.tab)))
print(div.tab, add.to.row = addtorow, include.colnames = FALSE, 
      comment = FALSE, hline.after = c(-1, -1, 0, nrow(div.tab)))
```

## Paired T-Tests
```{r}
div.2011 <- div.raw[div.raw$Year == "2011", ]
div.2012 <- div.raw[div.raw$Year == "2012", ]
t.test(div.2011$S.rar, div.2012$S.rar, paired = T)

div.D <- div.raw[div.raw$Molecule == "DNA", ]
div.R <- div.raw[div.raw$Molecule == "RNA", ]
t.test(div.D$S.rar, div.R$S.rar, paired = T)

mod1 <- lm(div.raw$S.rar ~ as.factor(div.raw$Lake) + 
             as.factor(div.raw$Year) + as.factor(div.raw$Molecule))
Anova(mod1)
```

## Calculate and Visualize Beta Diversity
```{r}
beta.w <- function(site1 = "", site2 = ""){
  site1 = subset(site1, select = site1 > 0)               # Removes absences
  site2 = subset(site2, select = site2 > 0)               # Removes absences
  gamma = union(colnames(site1), colnames(site2))         # Gamma species pool
  s     = length(gamma)                                   # Gamma richness
  a.bar = mean(c(specnumber(site1), specnumber(site2)))   # Mean sample richness
  b.w   = round(s/a.bar - 1, 3)
  return(b.w)
}

# Calculate Bray-Curtis 
hmwf.bray.PA <- vegdist(OTUsPA, method = "bray")
hmwf.bray.REL <- vegdist(OTUsREL, method = "bray")
hmwf.bray.Log <- vegdist(OTUsREL.log, method = "bray")

# Import UniFrac Distances
hmwf.uni.in <- read.table("../fasttree/HMWF.bac.0.03.gg.tree1.weighted.phylip.dist", skip=1, row.names = 1)
hmwf.uni <- as.dist(hmwf.uni.in)

OTU.tab <- otu_table(OTUsREL, taxa_are_rows = F)
OTU.tab.l <- otu_table(OTUsREL.log, taxa_are_rows = F)
PHY.tree <- phy_tree(hmwf.tree)
phylo.seq <- phyloseq(OTU.tab, PHY.tree)
phylo.seq.l <- phyloseq(OTU.tab.l, PHY.tree)
uni.frac.u <- UniFrac(phylo.seq, weighted = FALSE, normalized = TRUE)
uni.frac.w <- UniFrac(phylo.seq, weighted = TRUE, normalized = TRUE)
uni.frac.wl <- UniFrac(phylo.seq.l, weighted = TRUE, normalized = TRUE)
```

## Principal Coordinates Analysis 
```{r}
# Bray Curtis PA
pcoa.pa <- cmdscale(hmwf.bray.PA, eig = TRUE, k = 3) 
explainvar1.pa <- round(pcoa.pa$eig[1] / sum(pcoa.pa$eig), 3) * 100
explainvar2.pa <- round(pcoa.pa$eig[2] / sum(pcoa.pa$eig), 3) * 100
explainvar3.pa <- round(pcoa.pa$eig[3] / sum(pcoa.pa$eig), 3) * 100
sum.eig.pa <- sum(explainvar1.pa, explainvar2.pa, explainvar3.pa)

# Bray Curtis REL
pcoa.rel <- cmdscale(hmwf.bray.REL, eig = TRUE, k = 3) 
explainvar1.rel <- round(pcoa.rel$eig[1] / sum(pcoa.rel$eig), 3) * 100
explainvar2.rel <- round(pcoa.rel$eig[2] / sum(pcoa.rel$eig), 3) * 100
explainvar3.rel <- round(pcoa.rel$eig[3] / sum(pcoa.rel$eig), 3) * 100
sum.eig.rel <- sum(explainvar1.rel, explainvar2.rel, explainvar3.rel)

# Bray Curtis REL Log
pcoa.log <- cmdscale(hmwf.bray.Log, eig = TRUE, k = 3) 
explainvar1.log <- round(pcoa.log$eig[1] / sum(pcoa.log$eig), 3) * 100
explainvar2.log <- round(pcoa.log$eig[2] / sum(pcoa.log$eig), 3) * 100
explainvar3.log <- round(pcoa.log$eig[3] / sum(pcoa.log$eig), 3) * 100
sum.eig.log <- sum(explainvar1.log, explainvar2.log, explainvar3.log)

# UniFrac Unweighted
pcoa.ufu <- cmdscale(uni.frac.u, eig = TRUE, k = 3) 
explainvar1.ufu <- round(pcoa.ufu$eig[1] / sum(pcoa.ufu$eig), 3) * 100
explainvar2.ufu <- round(pcoa.ufu$eig[2] / sum(pcoa.ufu$eig), 3) * 100
explainvar3.ufu <- round(pcoa.ufu$eig[3] / sum(pcoa.ufu$eig), 3) * 100
sum.eig.ufu <- sum(explainvar1.ufu, explainvar2.ufu, explainvar3.ufu)

# UniFrac Weighted
pcoa.ufw <- cmdscale(uni.frac.w, eig = TRUE, k = 3) 
explainvar1.ufw <- round(pcoa.ufw$eig[1] / sum(pcoa.ufw$eig), 3) * 100
explainvar2.ufw <- round(pcoa.ufw$eig[2] / sum(pcoa.ufw$eig), 3) * 100
explainvar3.ufw <- round(pcoa.ufw$eig[3] / sum(pcoa.ufw$eig), 3) * 100
sum.eig.ufwl <- sum(explainvar1.ufw, explainvar2.ufw, explainvar3.ufw)

# UniFrac Weighted Log
pcoa.ufwl <- cmdscale(uni.frac.wl, eig = TRUE, k = 3) 
explainvar1.ufwl <- round(pcoa.ufwl$eig[1] / sum(pcoa.ufwl$eig), 3) * 100
explainvar2.ufwl <- round(pcoa.ufwl$eig[2] / sum(pcoa.ufwl$eig), 3) * 100
explainvar3.ufwl <- round(pcoa.ufwl$eig[3] / sum(pcoa.ufwl$eig), 3) * 100
sum.eig.ufwl <- sum(explainvar1.ufwl, explainvar2.ufwl, explainvar3.ufwl)
```

## Figure 2: Bacterial Community Composition Ordination Figures (Rel Abundance)
```{r, results='hide'}
design$Lake_Mol <- paste(design$Lake, design$Molecule, sep = "_")

# after specifying custom palette
palette(rainbow_hcl(10, c = 80, l = 60)) #[c(5, 2, 6, 3, 1)])
lake.col <- rep(NA, length(unique(design$Lake)))
names(lake.col) <- unique(design$Lake)
lake.col <- as.numeric(factor(design$Lake))

png(filename="../figures/Figure2.png",
    width = 1800, height = 900, res = 96*2)
par(opar)
# Define Plot Parameters
layout(matrix(c(1, 1, 2, 2,
                1, 1, 2, 2), ncol = 4, byrow = T))
layout.show(3)
par(mar = c(0, 0, 0, 0) + 0.5, oma = c(5, 5, 1, 1))

# Define Plot Symbols
lake.pch <- rep(NA, length(design$Molecule))
for (i in 1:length(design$Molecule)){
if (design$Molecule[i] == "DNA"){
    lake.pch[i] <- 16
  }else{
    lake.pch[i] <- 17
  }}

pcoa.plots <- list(pcoa.pa, pcoa.ufu, 
                   pcoa.rel, pcoa.ufw, 
                   pcoa.log, pcoa.ufwl)
explainvar1 <- c(explainvar1.pa, explainvar1.rel, explainvar1.log, explainvar1.ufu,
                 explainvar1.ufw, explainvar1.ufwl)
explainvar2 <- c(explainvar2.pa, explainvar2.rel, explainvar2.log, explainvar2.ufu,
                 explainvar2.ufw, explainvar2.ufwl)

xlabel <- c(F, F, T, T, T, T)
ylabel <- c(T, F, T, F, T, F)

for (i in (3:4)){
  # Initiate Plot
  plot(pcoa.plots[[i]]$points[ ,1], pcoa.plots[[i]]$points[ ,2], 
     ylim = c(-0.4, 0.4), xlim = c(-0.25, 0.55), 
     #xlab = paste("PCoA 1 (", explainvar1[i], "%)", sep = ""),
     #ylab = paste("PCoA 2 (", explainvar2[i], "%)", sep = ""),
     xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     pch = lake.pch, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1, 
     axes = FALSE)

  # Add Axes
  axis(side = 1, labels = xlabel[i], lwd.ticks = 2, cex.axis = 1, las = 1)
  axis(side = 2, labels = ylabel[i], lwd.ticks = 2, cex.axis = 1, las = 1)
  axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
  axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
  axis(side = 1, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 2, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  abline(h = 0, v = 0, lty = 3)
  box(lwd = 2)
  
  # Add Percent Explained
  #text
  
  # Add Points & Labels
  points(pcoa.plots[[i]]$points[ ,1], pcoa.plots[[i]]$points[ ,2], pch = lake.pch, 
         cex = 4, bg = "gray", col = lake.col)
  
  # Add Molecule Hulls
  ordihull(cbind(pcoa.plots[[i]]$points[ ,1], pcoa.plots[[i]]$points[ ,2]),
           design$Molecule, lwd=2, draw = "polygon", col="gray80", border = "black", 
           label=TRUE, cex=1, bty = 'n')
  
  # Add Y Axis Label  
  if (i == 3){
    mtext(side = 2, "PCoA 2", outer = F, line = 3)
  }
  
  # Add Molecule Legend to Plot 6
  if (i == 4){
    legend("bottomright", c("DNA", "RNA"), pch = c(16, 17), 
           col = "gray", bty = "n", pt.cex = 1.5, cex = 1.25)
    legend("topright", levels(design$Lake), ncol = 2, pch = 16, col = 1:10, 
           bty = "n", pt.cex = 1.5, cex = 1.25)
  }
}

mtext(side = 1, "PCoA 1", outer = T, line = 3)

# ordiellipse(cbind(hmwf.pcoa$points[ ,1], hmwf.pcoa$points[ ,2]),
#     design$Lake, kind="sd", conf=0.95,
#     lwd=2, draw = "polygon", col="gray", border = "black", label=TRUE, 
#     cex=1, bty = 'n')

#ordihull(cbind(hmwf.pcoa$points[ ,1], hmwf.pcoa$points[ ,2]),
#    design$Molecule, 
#    lwd=2, draw = "polygon", col="gray", border = "black", label=TRUE, 
#    cex=1, bty = 'n')

# Add Labels
# text(0.38, 0.13, "Lily")
# text(0.56, -0.11, "Pony")
# text(0.05, -0.19, "Upper Pine")
# text(-0.18, -0.29, "Second Pine")
# text(0, -0.05, "Mountain")
# text(-0.25, 0, "Ives")
# text(0.1, 0.1, "Canyon")
# text(-0.25, 0.1, "Howe")
# text(-0.2, 0.225, "Rush")
# text(-0.05, 0.2, "Ann")

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=4, fig.height=4,echo=FALSE,fig.cap="PCoA Plots"}
img <- readPNG("../figures/Figure2.png")
grid.raster(img)
```

## PERMANOVA
```{r}
beta.dis <- betadisper(vegdist(OTUsREL, "bray"), design$Lake)
permutest(beta.dis)

per.bray.pa <- adonis(OTUsPA ~ design$Lake + design$Molecule, method = "bray")
per.bray.rel <- adonis(OTUsREL ~ design$Lake + design$Molecule, method = "bray")
per.bray.l <- adonis(OTUsREL.log ~ design$Lake + design$Molecule, method = "bray")
per.uni.pa <- adonis(uni.frac.u ~ design$Lake + design$Molecule)
per.uni.rel <- adonis(uni.frac.w ~ design$Lake + design$Molecule)
per.uni.l <- adonis(uni.frac.wl ~ design$Lake + design$Molecule)
```

## PERMANOVA Table
```{r, results="asis"}
per.models <- data.frame(matrix(NA, ncol = 4, nrow = 6))
colnames(per.models) <- c("Lake R2", "Lake P", "Molecule R2", "Molecule P")
row.names(per.models) <- c("Bray-Curtis -- PA", "Bray-Curtis -- REL", "Bray-Curtis -- Log",
                    "UniFrac -- PA", "UniFrac -- REL", "UniFrac -- Log")
per.models[1, ] <- c(per.bray.pa$aov.tab$R2[1], per.bray.pa$aov.tab$`Pr(>F)`[1],
                     per.bray.pa$aov.tab$R2[2], per.bray.pa$aov.tab$`Pr(>F)`[2])
per.models[2, ] <- c(per.bray.rel$aov.tab$R2[1], per.bray.rel$aov.tab$`Pr(>F)`[1],
                     per.bray.rel$aov.tab$R2[2], per.bray.rel$aov.tab$`Pr(>F)`[2])
per.models[3, ] <- c(per.bray.l$aov.tab$R2[1], per.bray.l$aov.tab$`Pr(>F)`[1],
                     per.bray.l$aov.tab$R2[2], per.bray.l$aov.tab$`Pr(>F)`[2])
per.models[4, ] <- c(per.uni.pa$aov.tab$R2[1], per.uni.pa$aov.tab$`Pr(>F)`[1],
                     per.uni.pa$aov.tab$R2[2], per.uni.pa$aov.tab$`Pr(>F)`[2])
per.models[5, ] <- c(per.uni.rel$aov.tab$R2[1], per.uni.rel$aov.tab$`Pr(>F)`[1],
                     per.uni.rel$aov.tab$R2[2], per.uni.rel$aov.tab$`Pr(>F)`[2])
per.models[6, ] <- c(per.uni.l$aov.tab$R2[1], per.uni.l$aov.tab$`Pr(>F)`[1],
                     per.uni.l$aov.tab$R2[2], per.uni.l$aov.tab$`Pr(>F)`[2])

per.models[, c(1,3)] <- round(per.models[, c(1,3)], 2)

addtorow <- list()
addtorow$pos <- list(0, 0)
addtorow$command <- c("Model & \\multicolumn{2}{c}{Lake} & \\multicolumn{2}{c}{Molecule} \\\\\n", 
                      " & \\multicolumn{1}{c}{R\\textsuperscript{2}} & 
                          \\multicolumn{1}{c}{\\emph{P}} & 
                          \\multicolumn{1}{c}{R\\textsuperscript{2}} & 
                          \\multicolumn{1}{c}{\\emph{P}} \\\\\n")
per.tab <- xtable(per.models, auto = TRUE)
align(per.tab) <- c("l ","r ", "r ", "r ", "r ")
print(per.tab, add.to.row = addtorow, include.colnames = FALSE, 
      type= "latex", file="../tables/Table5.tex", 
      hline.after = c(-1, -1, 0, nrow(per.tab)))
print(per.tab, add.to.row = addtorow, include.colnames = FALSE, 
      comment = FALSE, hline.after = c(-1, -1, 0, nrow(per.tab)))
```


# Patterns of Resource Diversity
A major distinction of this project is the addition of organic matter diversity

## Import Raw Data
```{r}
# Define Inputs
# Resource = raw site-by-resource matrix
resource.pos <- "../data/SpecAbundAvePos.csv"
resource.neg <- "../data/SpecAbundAveNeg.csv"

# Import Resources
res.in <- read.csv(resource.neg, header=T, row.names=1)

rownames(res.in)
rownames(res.in) <- c("Ann", "blank", "CanyonChemo", "Canyon", "CanyonHypo",
                      "CanyonI", "CanyonII", "CanyonIII", "CanyonIV", "Howe",
                      "Ives", "Jordan", "Lily", "Mountain", "Pony", "Rush",
                      "SecondPine", "UpperPine")

blank <- unlist(res.in["blank", ])
res.hmwf <- res.in[-c(which(rownames(res.in) %in% c("blank", "CanyonChemo", 
                          "CanyonHypo", "CanyonI", "CanyonII",
                          "CanyonIII", "CanyonIV", "Jordan"))), ]
```

## Remove Major Peaks from Blanks
```{r}
summary(blank)
blank[which(blank > 2 * sd(blank))]

# res.hmwf <- res.hmwf[, -c(which(blank > sd(blank)))]

# What other peaks should be removed
for (i in 1:dim(res.hmwf)[1]){
  res.hmwf[i, ] <- res.hmwf[i, ] - blank * 1.1
}

res.hmwf[res.hmwf < 50] <- 0
res.hmwf <- res.hmwf[,colSums(res.hmwf) > 0]
```

## Data Transformations
```{r}
# Remove OTUs with less than two occurences across all sites
res <- res.hmwf

# Sequencing Coverage
coverage <- rowSums(res)

# # Remove Low Coverage Samples (This code removes two sites: Site 5DNA, Site 6cDNA)
# lows <- which(coverage < 10000)
# OTUs <- OTUs[-which(coverage < 10000), ]
# design <- design[-which(coverage < 10000), ]

# Make Relative Abundence Matrices
resREL <- res
for(i in 1:dim(res)[1]){
  resREL[i,] <- res[i,]/sum(res[i,])
}

# Log Transform Relative Resource Abundance
resREL.log <- decostand(resREL, method="log")
```

## Calculate Alpha Diversity
```{r}
# Observed Richness
S.res <- rowSums((res > 0) * 1)

# Simpson's Evenness
res.simpsE <- round(apply(res, 1, SimpE), 3)

# Shannon's Diversity
res.shan <- round(apply(res, 1, H), 2)
res.shan2 <- round(diversity(res, index = "shannon"), 2)

res.div <- as.data.frame(cbind(S.res, res.simpsE, res.shan2))
res.div
range(res.div$S.res)
range(res.div$res.shan2)
range(res.div$res.simpsE)
```

## Calculate and Visualize Resourde Beta Diversity
```{r}
# Calculate Bray-Curtis 
hmwf.bray.res <- vegdist(res, method = "bray")

dis.mean <- mean(hmwf.bray.res)

# Principal Coordinates Analysis
pcoa.res <- cmdscale(hmwf.bray.res, eig = TRUE, k = 3) 
explainvar1.res <- round(pcoa.res$eig[1] / sum(pcoa.res$eig), 3) * 100
explainvar2.res <- round(pcoa.res$eig[2] / sum(pcoa.res$eig), 3) * 100
explainvar3.res <- round(pcoa.res$eig[3] / sum(pcoa.res$eig), 3) * 100
sum.eig.res <- sum(explainvar1.res, explainvar2.res, explainvar3.res)
```

## Figure 3: Organic Matter Ordination Figures
```{r, results='hide'}
design2 <- design[design$Molecule == "DNA" & design$Year == "2012", ]
# Custom palette
palette(rainbow_hcl(10, c = 80, l = 60))
lake.col <- rep(NA, length(unique(design2$Lake)))
names(lake.col) <- unique(design2$Lake)
lake.col <- as.numeric(factor(design2$Lake))

png(filename="../figures/Figure4.png",
    width = 900, height = 900, res = 96*2)
par(opar)

# Define Plot Parameters
layout(matrix(1))
par(mar = c(5, 5, 0, 0) + 0.5)

plot(pcoa.res$points[ ,1], pcoa.res$points[ ,2], 
     ylim = c(-0.25, 0.35), xlim = c(-0.3, 0.3), 
     xlab = paste("PCoA 1 (", explainvar1.res, "%)", sep = ""),
     ylab = paste("PCoA 2 (", explainvar2.res, "%)", sep = ""),
     #xlab = "", ylab = "", 
     xaxt = "n", yaxt = "n",
     pch = 17, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1, 
     axes = FALSE)

  # Add Axes
  axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1, las = 1)
  axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1, las = 1)
  axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
  axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
  axis(side = 1, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 2, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  abline(h = 0, v = 0, lty = 3)
  box(lwd = 2)
  
# Add Points & Labels
points(pcoa.res$points[ ,1], pcoa.res$points[ ,2], pch = 17, 
       cex = 4, bg = "gray", col = lake.col)
text(pcoa.res$points[ ,1], pcoa.res$points[ ,2], labels = row.names(pcoa.res$points))


# mtext(side = 1, "PCoA 1", outer = T, line = 3)
# mtext(side = 2, "PCoA 2", outer = F, line = 3)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=4, fig.height=4,echo=FALSE,fig.cap="PCoA Plot Resources"}
img <- readPNG("../figures/Figure3.png")
grid.raster(img)
```

## Resource Diversity and Nutrient Concentrations
```{r}
nuts2012 <- nuts[nuts$year == "2012", ]
evenmod <- lm(res.div$res.simpsE ~ nuts2012$DOC*nuts2012$TN*nuts2012$TP)
richmod <- lm(res.div$S.res ~ nuts2012$DOC*nuts2012$TN*nuts2012$TP)
summary(evenmod)
summary(richmod)

evenmod <- lm(res.div$res.simpsE ~ log(nuts2012$DOC))
richmod <- lm(res.div$S.res ~ log(nuts2012$DOC))
summary(evenmod)
summary(richmod)
# Not using this because variation in resource alpha doesn't appear to be meaningful
```







## Distance Based Redundancy Analysis
```{r, results = 'hide'}
# Define Environmental Matrix
env.chem <- as.data.frame(scale(apply(nuts[,3:5], 2, log)))
row.names(env.chem) <- paste(nuts$sample, nuts$year, sep = "-")
env.chem <- as.data.frame(env.chem[sort(row.names(env.chem)), ])
env.chem.L <- env.chem[nuts$sample != "Pony" & nuts$sample != "Lily", ]
env.chem2012 <- as.data.frame(env.chem[grep("2012", row.names(env.chem)), ])

# Define DNA Community
OTUsREL.D <- OTUsREL[design$Molecule == "DNA" , ]

# Define RNA Community
OTUsREL.R <- OTUsREL[design$Molecule == "RNA" , ]

# Calculate Bray-Curtis Distances for Bacteria
Bray.REL.D <- vegdist(OTUsREL.D, "bray")
Bray.REL.R <- vegdist(OTUsREL.R, "bray")
 
# Calculate UniFrac Distances for Bacteria
OTU.tab.D <- otu_table(OTUsREL.D, taxa_are_rows = F)
OTU.tab.R <- otu_table(OTUsREL.R, taxa_are_rows = F)
PHY.tree <- phy_tree(hmwf.tree)
phylo.seq.D <- phyloseq(OTU.tab.D, PHY.tree)
phylo.seq.R <- phyloseq(OTU.tab.R, PHY.tree)
Uni.REL.D <- UniFrac(phylo.seq.D, weighted = TRUE, normalized = TRUE)
Uni.REL.R <- UniFrac(phylo.seq.R, weighted = TRUE, normalized = TRUE)

# Bray-Curtis Distances for Organic Matter
Bray.OM <- vegdist(res, "bray")

# Conduct dbRDA 
hmwf.bray.D.rda <- capscale(Bray.REL.D ~ env.chem$DOC + env.chem$TP + env.chem$TN, 
                            comm = OTUsREL.D, add = T)
hmwf.bray.R.rda <- capscale(Bray.REL.R ~ env.chem$DOC + env.chem$TP + env.chem$TN, 
                            comm = OTUsREL.R, add = T)
hmwf.uni.D.rda <- capscale(Uni.REL.R ~ env.chem$DOC + env.chem$TP + env.chem$TN, 
                           comm = OTUsREL.D, add = T)
hmwf.uni.R.rda <- capscale(Uni.REL.R ~ env.chem$DOC + env.chem$TP + env.chem$TN, 
                            comm = OTUsREL.R, add = T)
hmwf.res.rda <- capscale(Bray.OM ~ env.chem2012$DOC + env.chem2012$TP + env.chem2012$TN,
                         comm = res, add = T)

anova(hmwf.bray.D.rda)
RsquareAdj(hmwf.bray.D.rda)
anova(hmwf.bray.R.rda)
RsquareAdj(hmwf.bray.R.rda)
anova(hmwf.uni.D.rda)
RsquareAdj(hmwf.uni.D.rda)
anova(hmwf.uni.R.rda)
RsquareAdj(hmwf.uni.R.rda)
anova(hmwf.res.rda)
RsquareAdj(hmwf.res.rda)


```

## Figure 2: CCA Analysis
```{r, results='hide'}
png(filename="../figures/Figure3.png",
    width = 1800, height = 900, res = 96*2)
par(opar)
# Define Plot Parameters
layout(matrix(c(1:2), ncol = 2))
par(mar = c(5, 5, 4, 4) + 0.1)

# Initiate Plot 1
plot(scores(hmwf.bacD.cca, display = "wa"), xlim = c(-3, 3), ylim = c(-4, 4),
     xlab = paste("CCA 1 (", cca.D.explainvar1, "%)", sep = ""),
     ylab = paste("CCA 2 (", cca.D.explainvar2, "%)", sep = ""),
     pch = 16, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1.2, axes = FALSE)

# Add Axes
axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)

# Add Points & Labels
points(scores(hmwf.bacD.cca, display = "wa"),
       pch = 19, cex = 2, bg = "gray", col = lake.col)
#text(scores(hmwf.bacD.cca, display = "wa"), 
#     labels = row.names(scores(hmwf.bacD.cca, display = "wa")))

legend("bottomleft",levels(design$Lake), ncol = 1, pch = 16, col = 1:10, 
           bty = "n", pt.cex = 1, cex = 0.8)

# Add Environmental Vectors
vectors <- scores(hmwf.bacD.cca, display = "bp")
row.names(vectors) <- c("DOC", "TP", "TN")
arrows(0, 0, vectors[,1] * 2, vectors[, 2] * 2, 
       lwd = 2, lty = 1, length = 0.2, col = "red")
text(vectors[,1] * 2, vectors[, 2] * 2, pos = c(3, 1, 1), 
     labels = row.names(vectors), col = "red", cex = 0.8)
axis(side = 3, lwd.ticks=2, cex.axis=  0.8, las = 1, col = "red", lwd = 2.2,
     at = c(-0.5, 0, 0.5, 1, 1.5) * 2, 
     labels = c(-0.5, 0, 0.5, 1, 1.5), col.axis = "red")
axis(side = 4, lwd.ticks=2, cex.axis = 0.8, las = 1, col = "red", lwd = 2.2, 
     at = c(-1, 0, 1) * 2, 
     labels = c(-1, 0, 1), col.axis = "red")


# Initiate Plot 2
plot(scores(hmwf.bacR.cca, display = "wa"), xlim = c(-3, 3), ylim = c(-4, 4),
     xlab = paste("CCA 1 (", cca.R.explainvar1, "%)", sep = ""),
     ylab = paste("CCA 2 (", cca.R.explainvar2, "%)", sep = ""),
     pch = 16, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1.2, axes = FALSE)

# Add Axes
axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)

# Add Points & Labels
points(scores(hmwf.bacR.cca, display = "wa"),
       pch = 19, cex = 2, bg = "gray", col = lake.col)
#text(scores(hmwf.bacD.cca, display = "wa"), 
#     labels = row.names(scores(hmwf.bacD.cca, display = "wa")))

#legend("bottomleft",levels(design$Lake), ncol = 1, pch = 16, col = 1:10, 
#           bty = "n", pt.cex = 1, cex = 0.8)

# Add Environmental Vectors
vectors <- scores(hmwf.bacR.cca, display = "bp")
row.names(vectors) <- c("DOC", "TP", "TN")
arrows(0, 0, vectors[,1] * 2, vectors[, 2] * 2, 
       lwd = 2, lty = 1, length = 0.2, col = "red")
text(vectors[,1] * 2, vectors[, 2] * 2, pos = c(3, 1, 1), 
     labels = row.names(vectors), col = "red", cex = 0.8)
axis(side = 3, lwd.ticks=2, cex.axis=  0.8, las = 1, col = "red", lwd = 2.2,
     at = c(-0.5, 0, 0.5, 1, 1.5) * 2, 
     labels = c(-0.5, 0, 0.5, 1, 1.5), col.axis = "red")
axis(side = 4, lwd.ticks=2, cex.axis = 0.8, las = 1, col = "red", lwd = 2.2, 
     at = c(-1, 0, 1) * 2, 
     labels = c(-1, 0, 1), col.axis = "red")



dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=4, fig.height=4,echo=FALSE,fig.cap="PCoA Supplement"}
img <- readPNG("../figures/Figure2.png")
grid.raster(img)
```

## Variation Explained By The Concentration of Growth Limiting Resources
What are the differences between lakes and does resource concentration explain differences?

```{r}
env.chem2 <- as.data.frame(env.chem[rep(1:20, each = 2), ])

lake.dbrda <- capscale(OTUsREL.log ~ design$Lake + design$Molecule, distance = "bray", add = T)
anova(lake.dbrda)
RsquareAdj(lake.dbrda)
coef(lake.dbrda)

chem.dbrda <- capscale(OTUsREL ~ env.chem2$DOC + env.chem2$TP + env.chem2$TN, 
                       add = T, distance = "bray")
anova(chem.dbrda)
RsquareAdj(chem.dbrda)
coef(chem.dbrda)


cca(OTUsREL ~ env.chem2$DOC + env.chem2$TP + env.chem2$TN)
cca(OTUsREL ~ as.matrix(env.chem2))
capscale(OTUsREL ~ as.matrix(env.chem2), add = T, distance = "bray")
capscale(uni.frac.w ~ as.matrix(env.chem2), add = T)

anova.cca(chem.dbrda, step=1000)
plot(chem.dbrda)
lmod <- as.mlm(chem.dbrda)
# influence.measures(lmod)
lmod
summary(lmod)
```


## Species Distributions and Generalism
```{r}
lake.yr <- paste(design$Lake[design$Molecule == "DNA"], 
                 design$Year[design$Molecule == "DNA"], sep = "")

total <- OTUs[design$Molecule == "DNA", ]
row.names(total) <- lake.yr
totalPA <- (total > 0) * 1

active.rna <- OTUs[design$Molecule == "RNA", ]
row.names(active.rna) <- lake.yr
activePA <- (active.rna > 0) * 1
active <- total * (activePA)
row.names(active) <- lake.yr

activePA.2 <- (active.rna > (total * 0.25)) * 1
active.2 <- total * (activePA.2)
row.names(active.2) <- lake.yr

per <- c(0.001, 0.005, 0.01, 0.02, 0.03, 0.04, 0.05, 0.075, 0.10)
per.act <- matrix(NA, dim(total)[1], length(per))
per.actT <- matrix(NA, dim(total)[1], length(per))
colnames(per.act) <- per
colnames(per.actT) <- per

  for (i in 1:length(per)){
  activePA.temp <- (active.rna > (total * per[i])) * 1
  active.temp <- total * activePA.temp
  per.act[,i] <- rowSums(active.temp) / rowSums(total)
  per.actT[,i] <- rowSums(activePA.temp) / rowSums(totalPA)
  }

mean.per.act <- colMeans(per.act)
se.per.act <- apply(per.act, 2, se)

mean.per.actT <- colMeans(per.actT)
se.per.actT <- apply(per.actT, 2, se)
```

```{r, results= 'hide'}
png(filename="../figures/FigureZ.png",
    width = 900, height = 900, res = 96*2)
par(opar)
par(mar = c(4.5,5,1,1) + 0.1)
plot(mean.per.act ~ per, las = 1, type = "n",
     ylim = c(0.875, 0.99), 
     xaxt = "n", yaxt = "n", xlab = "", ylab = "")

arrows(x0 = per, y0 = mean.per.act, y1 = mean.per.act + se.per.act, angle= 90, length = 0.1, lwd = 2)
arrows(x0 = per, y0 = mean.per.act, y1 = mean.per.act - se.per.act, angle= 90, length = 0.1, lwd = 2)
points(per, mean.per.act, pch = 15, col = "firebrick", cex = 1.25)

axis(side=1, lwd.ticks = 2, tck=-0.02, labels = T, cex.axis = 1)
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1)
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1, las = 1, 
     at = c(0.89, 0.92, 0.95, 0.98))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(0.89, 0.92, 0.95, 0.98))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1)
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1)
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(0.89, 0.92, 0.95, 0.98))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(0.89, 0.92, 0.95, 0.98))
mtext(side = 2, "Percent Active", line = 3, cex = 1.5)
mtext(side = 1, "Cutoff", line = 2.5, cex = 1.5)
box(lwd = 2)
dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

## Generalist Taxa
```{r}
gens <- data.frame(matrix(NA, 21, 3))
colnames(gens) <- c("sites", "taxaA", "taxaT")
gens$sites <- c(1:21)

for (i in 1:21){
  gens$taxaA[i] <- sum(colSums(activePA) == i)
  gens$taxaT[i] <- sum(colSums(totalPA) == i)
}
```

## Generalists Plot
```{r, results= 'hide'}
png(filename="../figures/FigureY.png",
    width = 900, height = 900, res = 96*2)
par(opar)
# Define Plot Parameters
par(mar = c(5, 6, 1, 1) + 0.1)
plot(log10(gens$taxaT) ~ gens$sites, 
     yaxt = "n", xaxt = "n", ylab = "", xlab = "", las = 1,
     pch = 16, col = "cornflowerblue", xlim = c(0, 22), ylim = c(1, 3.8))
points(log10(gens$taxaA) ~ gens$sites, pch = 17, col = "darkolivegreen3")
     
mtext(side = 1, "Number of Sites", line = 3, cex = 1.5)
mtext(side = 2, "Number of Taxa", line = 3.5, cex = 1.5)
axis(side = 1, lwd = 2, labels = T)
axis(side = 2, lwd = 2, at = c(1, 2, 3, 3.7), labels = c(10, 100, 1000, 5000), las = 1)
axis(side = 3, lwd =2, tck = -0.02, labels = F)
axis(side = 4, lwd =2, tck = -0.02, labels = F, at = c(1, 2, 3, 3.7))
axis(side = 1, lwd =2, tck = 0.02, labels = F)
axis(side = 2, lwd =2, tck = 0.02, labels = F, at = c(1, 2, 3, 3.7))
axis(side = 3, lwd =2, tck = 0.02, labels = F)
axis(side = 4, lwd =2, tck = 0.02, labels = F, at = c(1, 2, 3, 3.7))
legend("topright", pch = c(16, 17), c("Total", "Active"), bty = "n", 
       col = c("cornflowerblue", "darkolivegreen3"))
box(lwd = 2)
dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r}
inactive <- total * (1 - activePA)
inactivePA <- (inactive > 0) * 1


# Inactive Taxa
inactivePA <- totalPA - activePA
inactive <- total * inactivePA
```

## Species Abundance Distribution for Active and Inactive
```{r, results= 'hide'}
png(filename="../figures/FigureX.png",
    width = 1200, height = 1000, res = 96*2)
par(opar)

par(mar = c(4, 5, 1, 1) + 0.1)
plot(sort(log10(colSums(active)), decreasing = T), col = "darkolivegreen3",
     las = 1, xaxt="n", xlab = "", yaxt="n", ylab = "", xlim = c(0, 7000))
points(sort(log10(colSums(inactive)), decreasing = T), col = "cornflowerblue")
axis(side=1, lwd.ticks = 2, tck=-0.02, labels = T, cex.axis = 1, at = c(0, 1500, 3000, 4500, 6000))
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(0, 1500, 3000, 4500, 6000))
axis(side=2, lwd.ticks = 2, labels = c("10", "1000", "100000"), cex.axis = 1, las = 1, 
     at = c(1, 3, 5))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1, 3, 5))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(0, 1500, 3000, 4500, 6000))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(0, 1500, 3000, 4500, 6000))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(1, 3, 5))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1, 3, 5))
mtext(side = 2, "Abundance", line = 3.5, cex = 1.5)
mtext(side = 1, "Index", line = 2.5, cex = 1)
legend("topright", c("Inactive", "Active"), fill = c("cornflowerblue", "darkolivegreen3"), bty = "n")
box(lwd = 2)
dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

## Data Checks
```{r}
pro.act <- rowSums(active)/rowSums(total)

rowSums(inactivePA)/rowSums(totalPA)
rowSums(activePA)/rowSums(totalPA)

plot(rowSums(activePA)/rowSums(totalPA), rowSums(inactivePA)/rowSums(totalPA))

inactive <- total * inactivePA
active.N <- total * (1-inactivePA)
active.NPA <- (active.N > 0 ) * 1

plot(rowSums(active.NPA)/rowSums(totalPA), rowSums(inactivePA)/rowSums(totalPA))
```

## Phosphorus Contributes to Activity
```{r, results= 'hide'}
png(filename="../figures/Figure6.png",
    width = 1200, height = 1000, res = 96*2)
par(opar)
par(mar=c(5, 5, 1, 1) + 0.1)
plot(rowSums(active.NPA)/rowSums(totalPA) ~ log10(nuts$TP[c(order(nuts$sample))]),
     xlab = expression(paste("Total Phosphorus (", mu , "g L"^-1, ")")),
     ylab = "Proportion of Active Taxa",
     las = 1, cex.lab = 1.5, xlim = c(0, 1.8), ylim = c(0.25, 0.75), xaxt = "n",
     pch = 15, col = "darkorchid4", cex = 1.5)
axis(side = 1, lwd = 2, at = c(0, 0.7, 1.7), labels = c(0, 5, 50))
axis(side = 2, lwd = 2, labels = F)
axis(side = 3, lwd = 2, tck = 0.02, labels = F, at = c(0, 0.7, 1.7))
axis(side = 4, lwd = 2, tck = 0.02, labels = F)
axis(side = 1, lwd = 2, tck = -0.02, labels = F, at = c(0, 0.7, 1.7))
axis(side = 2, lwd = 2, tck = -0.02, labels = F)
axis(side = 3, lwd = 2, tck = -0.02, labels = F, at = c(0, 0.7, 1.7))
axis(side = 4, lwd = 2, tck = -0.02, labels = F)
box(lwd = 2)
phos <- lm(rowSums(active.NPA)/rowSums(totalPA) ~ log10(nuts$TP[c(order(nuts$sample))]))
nitro <- lm(rowSums(active.NPA)/rowSums(totalPA) ~ log10(nuts$TN[c(order(nuts$sample))])) # NS
carb <- lm(rowSums(active.NPA)/rowSums(totalPA) ~ log10(nuts$DOC[c(order(nuts$sample))])) # NS
mod1 <- summary(phos)
abline(phos, lty = 2, lwd = 4, col = "darkred")
Rsq <- round(mod1$r.squared, 2)
Pv <- round(mod1$coefficients[2,4], 3)
text(1.5, 0.35, bquote(italic(R)^2 == .(format(Rsq, digits = 3))))
text(1.5, 0.3, bquote(italic(p) == .(format(Pv, digits = 3))))
dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=8, fig.height=5,echo=FALSE,fig.cap="Resource Alpha Diversity"}
img <- readPNG("../figures/Figure6.png")
grid.raster(img)
```



But there are other differences between these lakes. 
For example, algal derived resources differ (as infered from chlorophyll *a* concentrations).
Additionally, bacterial respiration differs between lakes though there is also temperature dependence with these values as well (temperature between years of sampling). 

# Ecosystem and Microbial Processes
```{r}
chla <- read.delim("../data/ChlorophyllA.txt")
resp <- read.delim("../data/Respiration.txt")
# npp
# CO2 flux
# EcoResp
# DO
```

## Table 3: Ecosystem and Microbial Processes
```{r, results="asis"}
eco <- data.frame(matrix(NA, 10, 4))
row.names(eco) <- levels(chla$Lake)
colnames(eco) <- c("Chl11", "Chl12", "Resp11", "Resp12")
for (i in row.names(eco)){
  eco[i, 1] <- round(mean(chla[chla$Lake == i & chla$Year == "2011", 3]), 2)
  eco[i, 2] <- round(mean(chla[chla$Lake == i & chla$Year == "2012", 3]), 2)
  eco[i, 3] <- round(mean(resp[resp$sample == i & resp$year == "2011", 4]), 3)    
  eco[i, 4] <- round(mean(resp[resp$sample == i & resp$year == "2012", 4]), 3)
}

addtorow <- list()
addtorow$pos <- list(0, 0, 0)
addtorow$command <- c(" & \\multicolumn{2}{c}{Chl $\\emph{a}$} & 
                      \\multicolumn{2}{c}{Resp.} \\\\\n", 
                      "Lake & \\multicolumn{2}{c}{($\\mu$g L$^{-1}$)} & 
                      \\multicolumn{2}{c}{($\\mu$M Hr$^{-1}$)} \\\\\n",
                      " & 2011 & 2012 & 2011 & 2012 \\\\\n")
eco.tab <- xtable(eco)
align(eco.tab) <- c("c ","r ", "r ", "r ", "r ")
print(eco.tab, add.to.row = addtorow, include.colnames = FALSE, 
      type= "latex", file="../tables/Table3.tex", 
      hline.after = c(-1, -1, 0, nrow(eco.tab)))
print(eco.tab, add.to.row = addtorow, include.colnames = FALSE, 
      comment = FALSE, hline.after = c(-1, -1, 0, nrow(eco.tab)))
```








## Hypothesis that resource diversity influences consumer diversity
```{r]}
alpha.div2012 <- alpha.div[alpha.div$Year == "2012" & alpha.div$Molecule == "RNA", c(1, 4:6)]
rownames(alpha.div2012) <- alpha.div2012[, 1]
alpha.div2012 <- alpha.div2012[, -1]
rownames(res.div) == rownames(alpha.div2012)

cor(res.div, alpha.div2012)

rich.mod1 <- lm(alpha.div2012$S.obs ~ res.div$S.res)
rich.mod2 <- lm(alpha.div2012$S.obs ~ res.div$res.simpsE)
summary(rich.mod1)
summary(rich.mod2)
```

```{r}
plot((rowSums(active.NPA)/rowSums(totalPA))[seq(2, 20, by = 2)] ~ res.div$res.simpsE,
     xlab = "Resource Evennes", ylab = "Proportion of Active Taxa")
res.ev <- lm((rowSums(active.NPA)/rowSums(totalPA))[seq(2, 20, by = 2)] ~ res.div$res.simpsE)
abline(res.ev)

```


## Between site comparisions of resources
```{r}
# Calculate Bray-Curtis 
res.db <- vegdist(resREL, method = "bray")

res.pcoa <- cmdscale(res.db, eig = TRUE, k = 3) 
explainvar1 <- round(res.pcoa$eig[1] / sum(res.pcoa$eig), 3) * 100
explainvar2 <- round(res.pcoa$eig[2] / sum(res.pcoa$eig), 3) * 100
explainvar3 <- round(res.pcoa$eig[3] / sum(res.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

# Define Plot Parameters
par(mar = c(5, 5, 1, 2) + 0.1)

# Plot Eigenvalues
plot(res.pcoa$eig, xlab = "PCoA Axis", ylab = "Eigenvalue", 
     las = 1, cex.lab = 1.5, pch = 16)

# Add Expectation based on Kaiser-Guttman criterion and Broken Stick Model
abline(h = mean(res.pcoa$eig), lty = 2, lwd = 2, col = "blue")
b.stick <- bstick(10, sum(res.pcoa$eig))
lines(1:10, b.stick, type = "l", lty = 4, lwd = 2, col = "red")

# Add Legend
legend("topright", legend = c("Avg Eigenvalue", "Broken-Stick"), 
       lty = c(2, 4), bty = "n", col = c("blue", "red"))
```


## Figre 6: Resource Differences Across Sites
```{r, results='hide'}
png(filename="../figures/Figure6.png",
    width = 1200, height = 1200, res = 96*2)

# Define Plot Parameters
par(mar = c(5, 5, 1, 1) + 0.1)

# Initiate Plot
plot(res.pcoa$points[ ,1], res.pcoa$points[ ,2], ylim = c(-0.25, 0.3),
     xlim = c(-0.4, 0.4), 
     xlab = paste("PCoA 1 (", explainvar1, "%)", sep = ""),
     ylab = paste("PCoA 2 (", explainvar2, "%)", sep = ""),
     pch = 16, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1.2, axes = FALSE)

# Add Axes
axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)

# Add Points & Labels
points(res.pcoa$points[ ,1], res.pcoa$points[ ,2],
       pch = 19, cex = 3, bg = "gray", col = "gray")
text(res.pcoa$points[ ,1], res.pcoa$points[ ,2], 
     labels = row.names(res.pcoa$points))
dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=8, fig.height=5,echo=FALSE,fig.cap="Resource Ordination"}
img <- readPNG("../figures/Figure6.png")
grid.raster(img)
```



## Resource Explainations of Differences
```{r}

OTUsREL2012.DNA <- OTUsREL[which(design$Year == "2012" & design$Molecule == "DNA"), ]
OTUsREL2012.DNA <- OTUsREL2012.DNA[ , colSums(OTUsREL2012.DNA > 0)]
OTUsREL2012.RNA <- OTUsREL[which(design$Year == "2012" & design$Molecule == "DNA"), ]
OTUsREL2012.RNA <- OTUsREL2012.RNA[ , colSums(OTUsREL2012.RNA > 0)]
active.N2012 <- active.N[grep("2012", rownames(active.N)), ]
rownames(OTUsREL2012.DNA) <- design$Lake[which(design$Year == "2012" & design$Molecule == "DNA")]
rownames(OTUsREL2012.RNA) <- design$Lake[which(design$Year == "2012" & design$Molecule == "DNA")]
rownames(active.N2012) <- design$Lake[which(design$Year == "2012" & design$Molecule == "DNA")]

# DNA
dbrda2012 <- capscale(OTUsREL2012.DNA ~ nuts2012$DOC + nuts2012$TN + nuts2012$TP, add =T, distance = "bray")
anova(dbrda2012)
RsquareAdj(dbrda2012)
coef(dbrda2012)

# RNA
dbrda2012 <- capscale(OTUsREL2012.RNA ~ nuts2012$DOC + nuts2012$TN + nuts2012$TP, add =T, distance = "bray")
anova(dbrda2012)
RsquareAdj(dbrda2012)
coef(dbrda2012)

# Active
dbrda2012 <- capscale(active.N2012 ~ nuts2012$DOC + nuts2012$TN + nuts2012$TP, add =T, distance = "bray")
anova(dbrda2012)
RsquareAdj(dbrda2012)
coef(dbrda2012)

# Resoruces
chem.dbrda <- capscale(resREL ~ nuts2012$DOC + nuts2012$TN + nuts2012$TP, add =T, distance = "bray")
anova(chem.dbrda)
RsquareAdj(chem.dbrda)
coef(chem.dbrda)

anova.cca(chem.dbrda, step=1000)
plot(chem.dbrda)
lmod <- as.mlm(chem.dbrda)
lmod
summary(lmod)

chem.dbrda <- capscale(resREL ~ log(nuts2012$DOC), add =T, distance = "bray")
anova(chem.dbrda)
RsquareAdj(chem.dbrda)
coef(chem.dbrda)

anova.cca(chem.dbrda, step=1000)
plot(chem.dbrda)
lmod <- as.mlm(chem.dbrda)
lmod
summary(lmod)



require(cocorresp)
#test1 <- coca(OTUsREL2012.RNA, resREL, n.axes = 4)

# Variance Partitioning

nuts3 <- cbind(scale(log(nuts2012$DOC)), scale(log1p(nuts2012$TP)))
# nuts3 <- scale(log(nuts2012$DOC))
rownames(nuts3) <- nuts2012$sample

res.db <- vegdist(resREL, method = "altGower")
res.pcoa <- cmdscale(res.db, eig = TRUE, k = 5) 

OTUsREL.log2012 <- OTUsREL.log[design$Year == "2012" & design$Molecule == "RNA", ]
OTUsREL2012 <- OTUsREL[design$Year == "2012" & design$Molecule == "RNA", ]
spe.pcoa <- cmdscale(vegdist(OTUsREL2012, method="bray"), eig = TRUE, k = 5)


# Active
HMWFvarpart <- varpart(spe.pcoa$points[, 1:2], nuts3, res.pcoa$points[, 1:2])
HMWFvarpart <- varpart(OTUsREL.log2012, nuts3, res.pcoa$points)
HMWFvarpart

png(filename="../figures/Figure7.png",
    width = 1200, height = 1200, res = 96*2)

plot(HMWFvarpart)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)

anova.cca(rda(spe.pcoa$points, nuts3), step=1000) #[a+b]
anova.cca(rda(spe.pcoa$points, res.pcoa$points), step=1000) #[b+c]
anova.cca(rda(spe.pcoa$points, cbind(nuts3, res.pcoa$points)), step=1000) #[a+b+c]
anova.cca(rda(spe.pcoa$points, res.pcoa$points, nuts3), step=1000) # [a]
anova.cca(rda(spe.pcoa$points, nuts3, res.pcoa$points), step=1000) # [c]

```

# Phylogenetic Approach










# Microbial Functional Groups

Define RDP microbial groups
Test each along with resource differences
Who are the generalist taxa (which are active everywhere)
Are generalists more abundant when resource concentration is higher?

# Can we group resources
What are the similar groups of resources: cluster resources based on abundance
Can we cluster based on chemical data?

```{r}

res.dist <- vegdist(t(resREL), "bray")

res2.pcoa <- cmdscale(res.dist, eig = TRUE, k = 3) 
explainvar1 <- round(res2.pcoa$eig[1] / sum(res2.pcoa$eig), 3) * 100
explainvar2 <- round(res2.pcoa$eig[2] / sum(res2.pcoa$eig), 3) * 100
explainvar3 <- round(res2.pcoa$eig[3] / sum(res2.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

# Define Plot Parameters
par(mar = c(5, 5, 1, 1) + 0.1)

# Initiate Plot
plot(res2.pcoa$points[ ,1], res2.pcoa$points[ ,2], ylim = c(-0.75, 0.75),
     xlim = c(-0.75, 0.75), 
     xlab = paste("PCoA 1 (", explainvar1, "%)", sep = ""),
     ylab = paste("PCoA 2 (", explainvar2, "%)", sep = ""),
     pch = 16, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1.2, axes = FALSE)

# Add Axes
axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1.2, las = 1)
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)

# Add Points & Labels
points(res2.pcoa$points[ ,1], res2.pcoa$points[ ,2],
       pch = 19, cex = 3, bg = "gray", col = "gray")
text(res2.pcoa$points[ ,1], res2.pcoa$points[ ,2], 
     labels = row.names(res.pcoa$points))


# Distances between molecules given sites
summary(resREL) # the data

# Calculate distances
res.dist <- vegdist(resREL, method = "bray")
res.dist2 <- vegdist(t(resREL), method = "bray")

res.pcoa <- cmdscale(res.dist2, eig = TRUE, k = 3) 



# Clustering
# res.k <- kmeans(resREL, 5, iter.max = 10)

# plot(resREL, col = res.k$cluster)



# Perform Cluster Analysis
res.ward <- hclust(res.dist, method = "ward.D2")
# Plot Cluster
par(mar = c(1, 5, 2, 2) + 0.1)
plot(res.ward, main = "Sites by Resource")

bac.dist <- vegdist(OTUsREL[design$Year == "2012" & 
                              design$Molecule == "DNA", ], method="bray")
bac.ward <- hclust(bac.dist, method = "ward.D2")
plot(bac.ward, main = "Sites by Species")

```








# Co-Occurance Analysis
```{r}
require("bioDist")

# Subset OTUs for to remove very rare taxa
OTUsREL2 <- OTUsREL[,which(colSums(as.matrix(OTUsREL)) > 0.05)]
resREL2 <- resREL[,which(colSums(as.matrix(resREL)) > 0.022)]

rownames(OTUsREL)
rownames(resREL)
OTUsREL3 <- OTUsREL2[grep("2012_RNA", rownames(OTUsREL)),]
OTUsREL3 <- OTUsREL3[,order(colSums(as.matrix(OTUsREL3)), decreasing = T)[1:100]]
resREL3 <- resREL2[,order(colSums(as.matrix(resREL2)), decreasing = T)[1:100]]
ConRes1 <- cbind(as.matrix(OTUsREL3), as.matrix(resREL3))
ConRes2 <- cbind(as.matrix(resREL3), as.matrix(OTUsREL3))
ConRes <- rbind(ConRes1, ConRes2)

# Calculate 1 - Spearman Correlation Coefficients: Spearman Distance
spear.bac <- spearman.dist(t(OTUsREL2), abs = FALSE)
spear.res <- spearman.dist(t(as.matrix(resREL2)), abs = FALSE)
spear.ConRes <- spearman.dist(t(as.matrix(ConRes)), abs = FALSE, diag = F, upper = F)

spear.bac2 <- spear.bac - 1
spear.bac3 <- spear.bac2
spear.bac3[which(spear.bac2 < 0.5 & spear.bac2 > -0.5)] <- NA

spear.res2 <- spear.res - 1
spear.res3 <- spear.res2
spear.res3[which(spear.res2 < 0.5 & spear.res2 > -0.5)] <- NA

spear.ConRes2 <- spear.ConRes - 1
spear.ConRes3 <- spear.ConRes2
spear.ConRes3[which(spear.ConRes2 < 0.5 & spear.ConRes2 > -0.5)] <- NA
spear.ConRes4 <- as.matrix(spear.ConRes3)[1:100, 101:200]

# Custome Color Palette
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", 
                                 "#7FFF7F", "yellow", "#FF7F00", "red", 
                                 "#7F0000"))


require(gridExtra)
order <- rev(attr(spear.bac3, "Labels"))
plot1 <- levelplot(as.matrix(spear.bac3)[,order], aspect = "iso", col.regions = jet.colors, 
          xlab = list(label = "OTU", cex = 1.2), ylab = list(label = "OTU", cex = 1.2), 
          scales = list(cex = 0.3, x = list(rot=90)),
          main = "Species Co-Occurence")
plot1

order <- rev(attr(spear.res3, "Labels"))
plot2 <- levelplot(as.matrix(spear.res3)[,order], aspect = "iso", col.regions = jet.colors, 
          xlab = list(label = "Resource", cex = 1.2), ylab = list(label = "Resource", cex = 1.2), 
          scales = list(cex = 0.3, x = list(rot=90)),
          main = "Resource Co-Occurence")

plot2



plot3 <- levelplot(spear.ConRes4, aspect = "iso", col.regions = jet.colors, 
          xlab = list(label = "Consumer", cex = 1.5), 
          ylab = list(label = "Resource", cex = 1.5), 
          scales = list(cex = 0.3, tck = 0.75,
                        #x = list(labels=colnames(ConRes)[1:100], rot=90),
                        #y = list(labels=colnames(ConRes)[101:200])),
                        x = list(rot=90),
                        y = list()),
          main = list(label = "Consumer-Resource Co-Occurence", line = 1),
          par.settings=list(layout.heights=list(top.padding=3, bottom.padding=3)))         
plot3
             
plot.new()       
             
spearB.pcoa <- cmdscale(spear.bac, eig = TRUE, k = 3) 
explainvar1 <- round(spearB.pcoa$eig[1] / sum(spearB.pcoa$eig), 3) * 100
explainvar2 <- round(spearB.pcoa$eig[2] / sum(spearB.pcoa$eig), 3) * 100
explainvar3 <- round(spearB.pcoa$eig[3] / sum(spearB.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

spearR.pcoa <- cmdscale(spear.res, eig = TRUE, k = 3) 
explainvar1 <- round(spearR.pcoa$eig[1] / sum(spearR.pcoa$eig), 3) * 100
explainvar2 <- round(spearR.pcoa$eig[2] / sum(spearR.pcoa$eig), 3) * 100
explainvar3 <- round(spearR.pcoa$eig[3] / sum(spearR.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

par(mar = c(5, 5, 1, 1) + 0.1)

# Define Plot Symbols
lake.pch <- rep(NA, length(design$Molecule))
for (i in 1:length(design$Molecule)){
if (design$Molecule[i] == "DNA"){
    lake.pch[i] <- 16
  }else{
    lake.pch[i] <- 17
  }}


# Initiate Plot
plot(spearB.pcoa$points[ ,1], spearB.pcoa$points[ ,2], 
     ylim = c(-0.4, 0.8), xlim = c(-0.5, 0.6), 
     xlab = paste("PCoA 1 (", explainvar1, "%)", sep = ""),
     ylab = paste("PCoA 2 (", explainvar2, "%)", sep = ""),
     pch = lake.pch, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1.2, 
     axes = FALSE)

# Add Axes
axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1, las = 1)
axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
axis(side = 1, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 2, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)

# Add Points & Labels
points(spearB.pcoa$points[ ,1], spearB.pcoa$points[ ,2],
       pch = lake.pch, cex = 0.5, bg = "gray", col = "gray")

#ordiellipse(cbind(spearB.pcoa$points[ ,1], spearB.pcoa$points[ ,2]),
 #   design$Lake, kind="sd", conf=0.95,
  #  lwd=2, draw = "polygon", col="gray", border = "black", label=TRUE, 
   # cex=1, bty = 'n')

spearR.pcoa <- cmdscale(spear.res, eig = TRUE, k = 3) 
explainvar1 <- round(spearR.pcoa$eig[1] / sum(spearR.pcoa$eig), 3) * 100
explainvar2 <- round(spearR.pcoa$eig[2] / sum(spearR.pcoa$eig), 3) * 100
explainvar3 <- round(spearR.pcoa$eig[3] / sum(spearR.pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2, explainvar3)

par(mar = c(5, 5, 1, 1) + 0.1)



# Initiate Plot
plot(spearR.pcoa$points[ ,1], spearR.pcoa$points[ ,2], 
     ylim = c(-0.4, 0.8), xlim = c(-0.5, 0.6), 
     xlab = paste("PCoA 1 (", explainvar1, "%)", sep = ""),
     ylab = paste("PCoA 2 (", explainvar2, "%)", sep = ""),
     pch = lake.pch, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1.2, 
     axes = FALSE)

# Add Axes
axis(side = 1, labels = T, lwd.ticks = 2, cex.axis = 1, las = 1)
axis(side = 2, labels = T, lwd.ticks = 2, cex.axis = 1, las = 1)
axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
axis(side = 1, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 2, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
abline(h = 0, v = 0, lty = 3)
box(lwd = 2)

# Add Points & Labels
points(spearR.pcoa$points[ ,1], spearR.pcoa$points[ ,2],
       pch = 17, cex = 0.5, bg = "gray", col = "gray")

```



## Cluster Lakes by Nutrients
```{r}
# nuts.m <- nuts[,3:5]
# row.names(nuts.m) <- paste(nuts[,1], nuts[,2], sep = "-")
# nuts.s <- t(scale(nuts.m))
# 
# # Determine number of clusters
# wss <- (nrow(nuts.s)-1)*sum(apply(nuts.s,2,var))
# for (i in 2:3) wss[i] <- sum(kmeans(nuts.s,
#    centers=i)$withinss)
# plot(1:15, wss, type="b", xlab="Number of Clusters",
#   ylab="Within groups sum of squares") 
# 
# # K-Means Cluster Analysis
# fit <- kmeans(nuts.s, 2) # 4 cluster solution
# # get cluster means
# aggregate(nuts.s,by=list(fit$cluster),FUN=mean)
# # append cluster assignment
# mydata <- data.frame(nuts.s, fit$cluster) 
# 
# 
# test <- hclust(dist(t(nuts.s)), method = "ward.D2")
# 
# # Ward Hierarchical Clustering with Bootstrapped p values
# library(pvclust)
# fit <- pvclust(t(nuts.s), method.hclust="ward.D2", method.dist = "euclidean")
# plot(fit) # dendogram with p values
# # add rectangles around groups highly supported by the data
# pvrect(fit, alpha=.95) 

```

## Supplemental Figure 2: Lake Nutrients
```{r, results='hide'}
png(filename="../figures/Supp2.png",
    width = 1600, height =1200, res = 96*2)
par(opar)
par(mfrow = c(1,1), mar = c(0, 6, 0, 0) + 0.5, oma = c(4, 0, 1, 1) + 0.5)
layout(rbind(1, 2, 3), height = c(3, 3, 3)) 

labs <- c("Ann", "Canyon", "Howe", "Ives", "Lily", "Mountain", "Pony", "Rush",
         "Second\nPine","Upper\nPine")

# DOC Plot
plot(DOC$conc ~ DOC$sample, ylim = c(0, 35), las = 1, 
     xaxt="n", xlab = "", yaxt="n", ylab = "")
axis(side=1, lwd.ticks = 2, tck = -0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=1, lwd.ticks = 2, tck = 0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1.2, las = 1, 
     at = c(0, 10, 20, 30))
axis(side=2, lwd.ticks = 2, tck = 0.01, labels = F, cex.axis = 1, 
     at = c(0, 10, 20, 30))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(0, 10, 20, 30))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0, 10, 20, 30))
mtext(side = 2, expression(paste("DOC (mg C L" ^-1, ")", sep="")), 
      line = 3.5, cex = 1)
legend("topleft", "A", bty = "n", x.intersp = 0, cex = 1.25)
box(lwd = 2)

# Total Nitrogen Plot
plot(TN$conc ~ TN$sample, ylim = c(0,2), las = 1, 
     xaxt="n", xlab = "", yaxt="n", ylab = "")
axis(side=1, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1.2, las = 1, 
     at = c(0.0, 0.5, 1.0, 1.5))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0.0, 0.5, 1.0, 1.5))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(0.0, 0.5, 1.0, 1.5))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0.0, 0.5, 1.0, 1.5))
mtext(side = 2, expression(paste("TN (mg N L" ^-1, ")")), 
      line = 3.5, cex = 1)
legend("topleft", "B", bty = "n", x.intersp = 0, cex = 1.25)
box(lwd = 2)

# Total Phosphorus Plot                       
plot(TP$sample, TP$conc, ylim = c(0,50), las = 1, 
     xaxt="n", xlab = "", yaxt="n", ylab = "")
axis(side=1, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1.2, las = 1, 
     at = c(0, 20, 40))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0, 20, 40))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(0, 20, 40))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0, 20, 40))
mtext(side = 2, expression(paste("TP (",mu, "g P L" ^-1, ")")), 
      line = 3.5, cex = 1)
mtext(side = 1, text = labs, line = 1, at = seq(1:10), padj = 0.5, cex = 0.8)
legend("topleft", "C", bty = "n", x.intersp = 0, cex = 1.25)
box(lwd = 2)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices 
par(opar)
```

```{r fig.width=6, fig.height=5,echo=FALSE,fig.cap="Lake Nutrients"}
# img <- readPNG("../figures/Supp2.png")
# grid.raster(img)
```

## Supplemental Figure 3: Ecosystem and Microbial Processes
```{r, results='hide'}
chla2 <- chla[chla$Year == "2012", ]
resp2 <- resp[resp$year == "2012", ]

png(filename="../figures/Supp3.png",
    width = 1600, height =1200, res = 96*2)
par(opar)
par(mfrow = c(1,1), mar = c(0, 6, 0, 0) + 0.5, oma = c(4, 0, 1, 1) + 0.5)
layout(rbind(1, 2), height = c(4, 4)) 

labs <- c("Ann", "Canyon", "Howe", "Ives", "Lily", "Mountain", "Pony", "Rush",
         "Second\nPine","Upper\nPine")

# ChlaA Plot 2012
plot(chla2$ChlA ~ chla2$Lake, ylim = c(0, 20), las = 1, 
     xaxt="n", xlab = "", yaxt="n", ylab = "")
axis(side=1, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(1:10))
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1:10))
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1.2, las = 1, 
     at = c(0, 10, 20))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0, 10, 20, 30))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(0, 10, 20, 30))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0, 10, 20, 30))
mtext(side = 2, expression(paste("Chl a (mg C L" ^-1, ")", sep="")), 
      line = 3.5, cex = 1)
legend("topleft", "A", bty = "n", x.intersp = 0, cex = 1.25)
box(lwd = 2)

# Bacterial Respiration
plot(resp2$rate ~ resp2$sample, ylim = c(0.5,2), las = 1, 
     xaxt="n", xlab = "", yaxt="n", ylab = "")
axis(side=1, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1.2, las = 1, 
     at = c(0, 1, 2))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0, 1, 2))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(1:10))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, 
     at = c(0, 1, 2))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, 
     at = c(0, 1, 2))
mtext(side = 2, expression(paste("Resp. (", mu, "M O"[2], " Hr" ^-1, ")")), 
      line = 3.5, cex = 1)
mtext(side = 1, text = labs, line = 1, at = seq(1:10), padj = 0.5, cex = 0.8)
legend("topleft", "B", bty = "n", x.intersp = 0, cex = 1.25)
box(lwd = 2)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices 
par(opar)
```

```{r fig.width=6, fig.height=5,echo=FALSE,fig.cap="Ecosystem"}
# img <- readPNG("../figures/Supp3.png")
# grid.raster(img)
```

## Supplemental Figure 4: Lake Bacterial Alpha Diversity
```{r, results='hide'}
png(filename="../figures/Supp4.png",
    width = 1600, height = 1100, res = 96*2)
par(opar)
par(mfrow = c(1,1), mar = c(0, 6, 0, 0) + 0.5, oma = c(3, 0, 1, 1) + 0.5)
layout(rbind(1, 2), height = c(3, 3)) 

labs <- c("Ann", "Canyon", "Howe", "Ives", "Lily", "Mountain", "Pony", "Rush",
         "Second\nPine","Upper\nPine")

plot(alpha.div$S.obs ~ alpha.div$Lake,  ylim = c(0,5000), las = 1, 
     xaxt="n", xlab = "", yaxt="n", ylab = "")
axis(side=1, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(1:10))
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1:10))
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1, las = 1, 
     at = c(1000, 3000, 5000))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1000, 3000, 5000, 7000))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(1:10))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1:10))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(1000, 3000, 5000, 7000))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1000, 3000, 5000, 7000))
mtext(side = 2, "Richness (S)", line = 4, cex = 1)
legend("topleft", "A", bty = "n", x.intersp = 0, cex = 1.25)
box(lwd = 2)

plot(alpha.div$simpsE ~ alpha.div$Lake, ylim = c(0,0.06), las = 1, 
     xaxt="n", xlab = "", yaxt="n", ylab = "")
axis(side=1, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(1:10))
axis(side=1, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1:10))
axis(side=2, lwd.ticks = 2, labels = T, cex.axis = 1, las = 1, 
     at = c(0, 0.02, 0.04, 0.06))
axis(side=2, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(0, 0.02, 0.04, 0.06))
axis(side=3, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(1:10))
axis(side=3, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(1:10))
axis(side=4, lwd.ticks = 2, tck=-0.02, labels = F, cex.axis = 1, at = c(0, 0.02, 0.04, 0.06))
axis(side=4, lwd.ticks = 2, tck=0.01, labels = F, cex.axis = 1, at = c(0, 0.02, 0.04, 0.06))
mtext(side = 2, "Simpson's Eveness (E)", line = 4, cex = 1)
mtext(side = 1, text = labs, line = 0.5, at = seq(1:10), padj = 0.5, cex = 0.8)
legend("topleft", "B", bty = "n", x.intersp = 0, cex = 1.25)
box(lwd = 2)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=6, fig.height=4,echo=FALSE,fig.cap="Lake Nutrients"}
# img <- readPNG("../figures/Supp4.png")
# grid.raster(img)
```

## Eigenvalue Analysis Plots
```{r}
png(filename="../figures/Supp5.png",
    width = 1600, height = 1100, res = 96*2)
# Define Plot Parameters
layout(as.matrix(cbind(1,2)))
par(mar = c(1, 1.5, 3, 1.5) + 0.1, oma = c(5, 5, 0.5, 0.5))

# Bray Curtis Analysis
# Plot Eigenvalues
plot(pcoa.rel$eig, main = "Bray Curtis", 
     #xlab = "PCoA Axis", ylab = "Eigenvalue", 
     las = 1, cex.lab = 1.5, pch = 16)

# Add Expectation based on Kaiser-Guttman criterion and Broken Stick Model
abline(h = mean(pcoa.rel$eig), lty = 2, lwd = 2, col = "blue")
b.stick <- bstick(42, sum(pcoa.rel$eig))
lines(1:42, b.stick, type = "l", lty = 4, lwd = 2, col = "red")

# Add Legend
legend("topright", legend = c("Avg Eigenvalue", "Broken-Stick"), 
       lty = c(2, 4), bty = "n", col = c("blue", "red"))

axis(1, lwd=2, labels = F)
axis(2, lwd=2, labels = F)
#axis(3, lwd=2, tck=-0.01, labels = F)
#axis(4, lwd=2, tck=-0.01, labels = F)
axis(1, lwd=2, tck=0.01, labels = F)
axis(2, lwd=2, tck=0.01, labels = F)
#axis(3, lwd=2, tck=0.01, labels = F)
#axis(4, lwd=2, tck=0.01, labels = F)

box(lwd=2)

# UniFrac Analysis
# Plot Eigenvalues
plot(pcoa.ufw$eig, main = "UniFrac", 
     #xlab = "PCoA Axis", ylab = "Eigenvalue", 
     las = 1, cex.lab = 1.5, pch = 16)

# Add Expectation based on Kaiser-Guttman criterion and Broken Stick Model
abline(h = mean(pcoa.ufw$eig), lty = 2, lwd = 2, col = "blue")
b.stick <- bstick(42, sum(pcoa.ufw$eig))
lines(1:42, b.stick, type = "l", lty = 4, lwd = 2, col = "red")

# Add Legend
legend("topright", legend = c("Avg Eigenvalue", "Broken-Stick"), 
       lty = c(2, 4), bty = "n", col = c("blue", "red"))

axis(1, lwd=2, labels = F)
axis(2, lwd=2, labels = F)
#axis(3, lwd=2, tck=-0.01, labels = F)
#axis(4, lwd=2, tck=-0.01, labels = F)
axis(1, lwd=2, tck=0.01, labels = F)
axis(2, lwd=2, tck=0.01, labels = F)
#axis(3, lwd=2, tck=0.01, labels = F)
#axis(4, lwd=2, tck=0.01, labels = F)

box(lwd=2)
mtext("PCoA Axis", side = 1, outer = T, line = 2.5, cex = 2)
mtext("Eigenvalue", side = 2, outer = T, line = 2.5, cex = 2)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=6, fig.height=4,echo=FALSE,fig.cap="Eigenvalue Analysis"}
img <- readPNG("../figures/Supp5.png")
grid.raster(img)
```


## Supplemental Figure 6: PCoA w/ All Distances
```{r, results='hide'}
png(filename="../figures/Supp6.png",
    width = 1800, height = 1800, res = 96*2)
par(opar)

# Define Plot Parameters
layout(matrix(c(7, 7, 7, 7,
                1, 1, 2, 2,
                1, 1, 2, 2,
                3, 3, 4, 4,
                3, 3, 4, 4,
                5, 5, 6, 6,
                5, 5, 6, 6), ncol = 4, byrow = T))
par(mar = c(0, 0, 0, 0) + 0.5, oma = c(4, 4, 1, 1))

# Define Plot Symbols
lake.pch <- rep(NA, length(design$Molecule))
for (i in 1:length(design$Molecule)){
if (design$Molecule[i] == "DNA"){
    lake.pch[i] <- 16
  }else{
    lake.pch[i] <- 17
  }}

pcoa.plots <- list(pcoa.pa, pcoa.ufu, 
                   pcoa.rel, pcoa.ufw, 
                   pcoa.log, pcoa.ufwl)
explainvar1 <- c(explainvar1.pa, explainvar1.rel, explainvar1.log, explainvar1.ufu,
                 explainvar1.ufw, explainvar1.ufwl)
explainvar2 <- c(explainvar2.pa, explainvar2.rel, explainvar2.log, explainvar2.ufu,
                 explainvar2.ufw, explainvar2.ufwl)

xlabel <- c(F, F, F, F, T, T)
ylabel <- c(T, F, T, F, T, F)

for (i in (1:length(pcoa.plots))){
  # Initiate Plot
  plot(pcoa.plots[[i]]$points[ ,1], pcoa.plots[[i]]$points[ ,2], 
     ylim = c(-0.4, 0.4), xlim = c(-0.25, 0.55), 
     #xlab = paste("PCoA 1 (", explainvar1[i], "%)", sep = ""),
     #ylab = paste("PCoA 2 (", explainvar2[i], "%)", sep = ""),
     xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     pch = lake.pch, cex = 2.0, type = "n", cex.lab = 1.5, cex.axis = 1, 
     axes = FALSE)

  # Add Axes
  axis(side = 1, labels = xlabel[i], lwd.ticks = 2, cex.axis = 1, las = 1)
  axis(side = 2, labels = ylabel[i], lwd.ticks = 2, cex.axis = 1, las = 1)
  axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
  axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=-0.02)
  axis(side = 1, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 2, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 3, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  axis(side = 4, labels = F, lwd.ticks = 2, cex.axis = 1, las = 1, tck=0.01)
  abline(h = 0, v = 0, lty = 3)
  box(lwd = 2)
  
  # Add Percent Explained
  
  # Add Points & Labels
  points(pcoa.plots[[i]]$points[ ,1], pcoa.plots[[i]]$points[ ,2], pch = lake.pch, 
         cex = 2.5, bg = "gray", col = lake.col)
  
  # Add Molecule Hulls
  ordihull(cbind(pcoa.plots[[i]]$points[ ,1], pcoa.plots[[i]]$points[ ,2]),
           design$Molecule, lwd=2, draw = "polygon", col="gray80", border = "black", 
           label=TRUE, cex=1, bty = 'n')
  
  # Add Y Axis Label  
  if (i == 3){
    mtext(side = 2, "PCoA 2", outer = F, line = 2.5)
  }
  
  # Add Molecule Legend to Plot 6
  if (i == 6){
    legend("topright", c("DNA", "RNA"), pch = c(16, 17), 
           col = "gray", bty = "n", pt.cex = 1.25)
  }
  
}
  
plot.new()
# par(mar = c(0, 0, 5, 0) + 0.5)
legend("center", levels(design$Lake), ncol = 5, pch = 16, col = 1:10, bty = "n")
mtext(side = 1, "PCoA 1", outer = T, line = 2)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=4, fig.height=4,echo=FALSE,fig.cap="PCoA Supplement"}
img <- readPNG("../figures/Supp6.png")
grid.raster(img)
```

## Supplemental Figure 5: Resource Diversity
```{r, results='hide'}
png(filename="../figures/SuppX.png",
    width = 1600, height = 1200, res = 96*2)
par(opar)
par(mfrow = c(1,1), mar = c(0, 9, 0, 0) + 0.5, oma = c(5, 0, 1, 1) + 0.5)
layout(rbind(1, 2, 3), height = c(3, 3, 3)) 
labs <- c("Ann", "Canyon", "Howe", "Ives", "Lily", "Mountain", "Pony", "Rush",
         "Second\nPine","Upper\nPine")
rich <- barplot(res.div$S.res, names.arg = NULL, las =1, ylim=c(0, 750), 
     xlab = "", ylab = "")
mtext(side = 2, text = "Resource\nRichness", cex.lab = 1.2, line = 4.5)
even <- barplot(res.div$res.simpsE, names.arg = NULL, las =1, ylim=c(0, 0.27), 
     xlab = "", ylab = "")
mtext(side = 2, text = "Simpson's\nEvenness", cex.lab = 1.2, line = 4.5)
shan <- barplot(res.div$res.shan, names.arg = NULL, las = 1, ylim = c(0, 9), 
     xlab = "", ylab = "")
mtext(side = 2, text = "Shannon\nDiversity", cex.lab = 1.2, line = 4.5)
mtext(side = 1, text = labs, line = 2, at = shan, padj = 0.5, cex = 0.8)

dev.off() # this writes plot to folder
graphics.off() # shuts down open devices
par(opar)
```

```{r fig.width=8, fig.height=5,echo=FALSE,fig.cap="Resource Alpha Diversity"}
img <- readPNG("../figures/SuppX.png")
grid.raster(img)
```
